---
title: "Example Charts for Fitbit Dashboard"
author: "Salome"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# SET UP WORKBOOK 
library(tidyverse)
library(lubridate)
library(plotly)
library(scales)
library(zoo)
library(knitr)
library(see)
```



```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Source colour palette
# source("R/colours.R")

# R/colours.R
# Okabe-Ito color palette - Colorblind accessible
# Source: Okabe, M., & Ito, K. (2008)

# Data colors - mapped to metrics
clr <- list(
  hr       = "#D55E00",  # vermillion
  steps    = "#0072B2",  # blue
  deep     = "#009E73",  # green
  light    = "#56B4E9",  # lightblue
  rem      = "#CC79A7",  # purple
  wake     = "#E69F00",  # orange
  calories = "#F5C710",  # yellow
  spo2     = "#009E73",  # green
  bg       = "#FFFFFF",  # white
  
  fat_burn = "#56B4E9",  # lightblue
  cardio   = "#F5C710",  # yellow
  peak     = "#D55E00",  # vermillion
  
  avg      = "#D55E00",  # vermillion
  min      = "#009E73",  # green
  sum      = "#56B4E9",  # lightblue
  max      = "#E69F00",  # orange
  
  text_primary   = "#000000",  # black
  text_secondary = "#999999",  # grey
  
  target_line = "#999999",  # grey
  grid_line   = "#E5E7EB",  # lightgrey
  error_bar   = "#999999",  # grey
  
  # Okabe-Ito color definitions
  black      = "#000000",
  orange     = "#E69F00",
  lightblue  = "#56B4E9",
  green      = "#009E73",
  yellow     = "#F5C710",
  blue       = "#0072B2",
  vermillion = "#D55E00",
  purple     = "#CC79A7",
  grey       = "#999999",
  white      = "#FFFFFF",
  lightgrey  = "#E5E7EB"
)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Load all CSV files from csvdata ------------------------------------

# Get list of all CSV files in csvdata folder
csv_files <- list.files("csvdata", pattern = "\\.csv$", full.names = FALSE)

# Remove .csv extension to use as variable names
file_names <- gsub("\\.csv$", "", csv_files)

# Load each file into a variable with the same name
for (i in seq_along(csv_files)) {
  file_path <- file.path("csvdata", csv_files[i])
  var_name <- file_names[i]
  assign(var_name, read.csv(file_path, stringsAsFactors = FALSE))
  #cat("Loaded:", var_name, "-", nrow(get(var_name)), "rows\n")
}
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Helper functions -----------------------------------------

# SANITIZE COLUMN NAMES: Handle old CSV files and standardize naming
# This ensures compatibility whether data was generated by new or old Excel scripts
sanitize_column_names <- function(df) {
  names(df) <- gsub("-", "_", names(df))
  names(df) <- sub("^participantId$", "participantID", names(df))
  return(df)
}

# Apply column name sanitization to all loaded data frames
# This fixes: hyphens → underscores, and "participantId" → "participantID"
all_data_frames <- ls()[sapply(ls(), function(x) is.data.frame(get(x)))]
for (df_name in all_data_frames) {
  df <- get(df_name)
  df_cleaned <- sanitize_column_names(df)
  assign(df_name, df_cleaned)
  # Report what changed (optional)
  if (!identical(names(df), names(df_cleaned))) {
    #cat("✓ Sanitized column names in:", df_name, "\n")
  }
}

# Helper: Convert date+time columns to datetime (handles 1899 Excel bug)
add_datetime_column <- function(df) {
  if (!is.null(df) && nrow(df) > 0 && "date" %in% names(df) && "time" %in% names(df)) {
    df %>%
      mutate(
        # Extract HH:MM:SS if present; if bare date only (midnight), use "00:00:00"
        time_clean = case_when(
          str_detect(time, "\\d{2}:\\d{2}:\\d{2}") ~ str_extract(time, "\\d{2}:\\d{2}:\\d{2}"),
          TRUE ~ "00:00:00"   # bare "1899-12-31" = midnight
        ),
        datetime = as.POSIXct(paste(date, time_clean), 
                              format = "%Y-%m-%d %H:%M:%S", tz = "UTC")
      ) %>%
      select(-time_clean)
  } else {
    df
  }
}

# Helper: Convert ISO timestamp to datetime (used by HRV, sessions, etc.)
add_datetime_from_timestamp <- function(df, timestamp_col = "timestamp") {
  if (!is.null(df) && nrow(df) > 0 && timestamp_col %in% names(df)) {
    df$datetime <- as.POSIXct(df[[timestamp_col]], format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
  }
  return(df)
}

#' Zero-fill a sparse intraday dataframe to a complete 5-minute grid
#' Adds rows with value = 0 for any missing 5-min slot within each date
zero_fill_5min <- function(df, value_col) {
  df %>%
    mutate(date_only = as.Date(datetime)) %>%
    group_by(participantID, date_only) %>%
    complete(
      datetime = seq(
        from = as.POSIXct(paste(unique(date_only), "00:00:00"), tz = "UTC"),
        to   = as.POSIXct(paste(unique(date_only), "23:55:00"), tz = "UTC"),
        by   = "5 min"
      )
    ) %>%
    mutate(across(all_of(value_col), ~ replace_na(., 0))) %>%
    ungroup() %>%
    select(-date_only)
}

# Helper function for empty plots
create_empty_plot <- function(message = "No data available") {
  # Create a simple empty plot with a message
  p <- ggplot() + 
    annotate("text", x = 0.5, y = 0.5, 
             label = message, 
             size = 5, 
             color = clr$text_secondary,
             hjust = 0.5) +
    theme_void() +
    theme(
      plot.background = element_rect(fill = clr$bg, color = NA),
      panel.background = element_rect(fill = clr$bg, color = NA)
    )
  
  # Return as plotly for consistency with other charts
  ggplotly(p) %>%
    layout(
      hoverlabel = list(bgcolor = clr$bg),
      margin = list(l = 20, r = 20, t = 20, b = 20)
    )
}
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Theme ------------------------
dash_theme <- function() {
  theme_minimal() +
    theme(
      # Grid lines - subtle
      panel.grid.major = element_line(color = clr$grid_line, linewidth = 0.3),
      panel.grid.minor = element_blank(),
      
      # Axis text
      axis.text = element_text(size = 10, color = clr$text_secondary),
      axis.title = element_text(size = 11, color = clr$text_secondary, face = "bold"),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)),
      
      # Legend
      legend.position = "bottom",
      legend.text = element_text(size = 10, color = clr$text_secondary),
      legend.title = element_blank(),
      
      # Title
      plot.title = element_text(size = 14, face = "bold", color = clr$text_primary, margin = margin(b = 10)),
      
      # Background - transparent for CSS compatibility
      plot.background = element_rect(fill = "transparent", color = NA),
      panel.background = element_rect(fill = "transparent", color = NA),
      legend.background = element_rect(fill = "transparent", color = NA)
    )
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Prepare HR data (date+time columns)
hr_data <- hr_intraday_5m %>%
  add_datetime_column() %>%
  filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220)

# Prepare Steps data (date+time columns)
steps_data <- steps_intraday_5m %>%
  add_datetime_column() %>%
  filter(!is.na(datetime))

# Prepare Distance data (date+time columns)
if (exists("distance_intraday")) {
  distance_data <- distance_intraday %>%
    add_datetime_column() %>%
    filter(!is.na(datetime))
}

# Prepare Activity Level data (date+time columns)
activity_level_data <- activity_level_intraday %>%
  add_datetime_column() %>%
  filter(!is.na(datetime))

# Prepare Zone Minutes data (date+time columns)
zone_data <- zone_minutes_intraday_5m %>%
  add_datetime_column() %>%
  filter(!is.na(datetime))

# Prepare HRV data (timestamp column - different format!)
hrv_data <- hrv_intraday %>%
  add_datetime_from_timestamp() %>%
  filter(!is.na(datetime), rmssd_ms > 0, rmssd_ms < 200)

# Add rolling average for HRV (as in app.R)
hrv_data <- hrv_data %>%
  arrange(datetime) %>%
  mutate(
    rolling_avg = zoo::rollapply(rmssd_ms, width = min(10, n()), 
                                 FUN = mean, fill = NA, align = "center")
  )

# Prepare Sleep data (ensure date column is proper Date type)
sleep_data <- sleep_minute %>%
  mutate(dateOfSleep = as.Date(dateOfSleep))

# Prepare Activity Sessions (needs start/end datetimes)
if (exists("activity_sessions")) {
  activity_sessions_data <- activity_sessions %>%
    mutate(
      start_datetime = as.POSIXct(start_time, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
      end_datetime = as.POSIXct(end_time, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
    ) %>%
    filter(!is.na(start_datetime))
}

# Prepare Sedentary Periods (needs start/end datetimes)
if (exists("sedentary_periods")) {
  sedentary_data <- sedentary_periods %>%
    mutate(
      start_datetime = as.POSIXct(period_start, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
      end_datetime = as.POSIXct(period_end, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
    ) %>%
    filter(!is.na(start_datetime))
}

# Prepare SpO2 data (with validation bounds)
if (exists("spo2_intraday")) {
  spo2_data <- spo2_intraday %>%
    add_datetime_from_timestamp() %>%
    filter(!is.na(datetime), value > 70, value < 100)  # Remove invalid readings
}

# Prepare Breathing Rate data
if (exists("breathing_rate_summary")) {
  breathing_data <- breathing_rate_summary %>%
    mutate(date = as.Date(date))
}
```

## Overview Tab

### 1-4. Overview KPI's

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== KPI: Average Heart Rate =====
if (exists("hr_data") && !is.null(hr_data) && nrow(hr_data) > 0) {
  avg_hr <- mean(hr_data$heart_rate_avg, na.rm = TRUE)
  kpi_hr <- round(avg_hr)
} else {
  kpi_hr <- NA
}

# ===== KPI: Average Daily Steps =====
if (exists("steps_data") && !is.null(steps_data) && nrow(steps_data) > 0) {
  daily_steps <- steps_data %>%
    mutate(date = as.Date(date)) %>%
    group_by(date) %>%
    summarise(total = sum(steps_5min, na.rm = TRUE))
  kpi_steps <- round(mean(daily_steps$total, na.rm = TRUE))
} else {
  kpi_steps <- NA
}

# ===== KPI: Average Deep Sleep =====
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  deep_by_night <- sleep_data %>%
    filter(sleep_stage == "deep") %>%
    group_by(dateOfSleep) %>%
    summarise(deep_minutes = n())
  kpi_sleep <- round(mean(deep_by_night$deep_minutes, na.rm = TRUE), 0)
} else {
  kpi_sleep <- NA
}

# ===== KPI: Average SpO2 =====
if (exists("spo2_data") && !is.null(spo2_data) && nrow(spo2_data) > 0) {
  kpi_spo2 <- round(mean(spo2_data$value, na.rm = TRUE), 1)
} else {
  kpi_spo2 <- NA
}

overview_kpi_table <- data.frame(
  Metric = c("Average Daily Heart Rate", "Average Daily Steps", "Average Deep Sleep", "Average SpO2"),
  Value = c(
    paste(kpi_hr, "bpm"),
    paste(format(kpi_steps, big.mark = ","), "steps"),
    paste(kpi_sleep, "min"),
    paste(kpi_spo2, "%")
  )
)

kable(overview_kpi_table)  # FIXED: Changed from kpi_table to overview_kpi_table
```

### 5. Heart Rate Over Time

Heart rate values over time shows daily patterns, resting HR trends, exercise intensity periods, and potential recovery patterns. This chart shows all days by averaged 5 minute buckets.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# For Rmd: use full dataset
# For App.R: hr_data() is already filtered by date and participant
if (exists("hr_data") && !is.null(hr_data) && nrow(hr_data) > 0) {
  chart_data <- hr_data %>%
    filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220)
  
  # Optional: Filter to specific date range if needed
  # chart_data <- chart_data %>%
  #   filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08"))
}

# ===== CHART CODE =====
# Create the ggplot object
if (exists("chart_data") && !is.null(chart_data) && nrow(chart_data) > 0) {
  hr_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = heart_rate_avg)) +
    # Raw data line - thin, semi-transparent
    geom_line(color = clr$hr, linewidth = 0.5, alpha = 0.8) +
    # Labels with clear descriptions
    labs(
      # title = "Heart Rate Over Time",
      x = NULL,
      y = "bpm"
      # To remove any label (title, x, or y), comment out or delete the line above
      # Example - to remove title only:
      # title = NULL, x = NULL, y = "bpm"
    ) +
    # Center the title
    theme(
      plot.title = element_text(hjust = 0.5)
    ) +
    dash_theme()
  
  # Convert to interactive plotly
  ggplotly(hr_timeseries_plot, tooltip = c("x", "y")) %>%
    layout(
      hoverlabel = list(bgcolor = clr$bg),
      title = list(text = "Heart Rate Over Time", x = 0.5),
      margin = list(l = 50, r = 20, t = 50, b = 40)
    )
} else {
  create_empty_plot("No heart rate data available")
}

# ===== FOR APP.R: Add to UI =====
# To use shinyfullscreen package to allow shiny app charts to full screen,
# we added library(shinyfullscreen) to app.R and we need to wrap the plotlyOutput
# in the UI section like this:
#
# shinyfullscreen::fullscreen_this(
#         plotlyOutput("plot_hr"),
#         click_to_fullscreen = TRUE
# )
#
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$plot_hr <- renderPlotly({
#   req(hr_data())
#   
#   df <- hr_data()
#   if (is.null(df) || nrow(df) == 0) {
#     return(create_empty_plot("No heart rate data available"))
#   }
#   
#   p <- ggplot(df, aes(x = datetime, y = heart_rate_avg)) +
#     geom_line(color = clr$hr, linewidth = 0.5, alpha = 0.8) +
#     labs(x = NULL, y = "bpm") +
#     # To remove title, add: title = NULL
#     # labs(title = NULL, x = NULL, y = "bpm")
#     dash_theme()
#   
#   ggplotly(p) %>% 
#     layout(hoverlabel = list(bgcolor = clr$bg),
#            margin = list(l = 50, r = 20, t = 50, b = 40))
# })
```

### 6. Daily Steps

Daily step count with 10,000 step target line. Helps track physical activity levels and identify days meeting activity goals. This chart shows all days by summed 5 minute buckets.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# Aggregate steps by day
if (exists("steps_data") && !is.null(steps_data) && nrow(steps_data) > 0) {
  daily_steps_chart <- steps_data %>%
    mutate(date = as.Date(date)) %>%
    group_by(date) %>%
    summarise(total = sum(steps_5min, na.rm = TRUE))
  
  # Optional: Filter to specific date range if needed
  # daily_steps_chart <- daily_steps_chart %>%
  #   filter(date >= as.Date("2026-05-28"), date <= as.Date("2026-06-08"))
}

# ===== CHART CODE =====
if (exists("daily_steps_chart") && !is.null(daily_steps_chart) && nrow(daily_steps_chart) > 0) {
  steps_plot <- ggplot(daily_steps_chart, aes(x = date, y = total)) +
    geom_col(fill = clr$steps, width = 0.7, alpha = 0.9) +
    geom_hline(yintercept = 10000, linetype = "dashed", 
               color = clr$target_line, linewidth = 0.5) +
    scale_y_continuous(labels = scales::comma) +
    scale_x_date(date_labels = "%b %d") +
    labs(x = NULL, y = "steps") +
    theme(plot.title = element_text(hjust = 0.5))+
    dash_theme()
  
  # Convert to interactive plotly
  ggplotly(steps_plot, tooltip = c("x", "y")) %>%
    layout(
      hoverlabel = list(bgcolor = clr$bg),
      title = list(text = "Daily Steps Over Time", x = 0.5),
      margin = list(l = 50, r = 20, t = 50, b = 40)
    )
} else {
  create_empty_plot("No steps data available")
}

# ===== FOR APP.R: Add to UI =====
# shinyfullscreen::fullscreen_this(
#   plotlyOutput("plot_steps"),
#   click_to_fullscreen = TRUE
# )
#
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$plot_steps <- renderPlotly({
#   req(steps_data())
#   
#   df <- steps_data()
#   if (is.null(df) || nrow(df) == 0) {
#     return(create_empty_plot("No steps data available"))
#   }
#   
#   daily_steps <- df %>%
#     mutate(date = as.Date(date)) %>%
#     group_by(date) %>%
#     summarise(total = sum(steps_5min, na.rm = TRUE))
#   
#   if (nrow(daily_steps) == 0) {
#     return(create_empty_plot("No steps data for selected date range"))
#   }
#   
#   p <- ggplot(daily_steps, aes(x = date, y = total)) +
#     geom_col(fill = clr$steps, width = 0.7, alpha = 0.9) +
#     geom_hline(yintercept = 10000, linetype = "dashed", 
#                color = "#9CA3AF", linewidth = 0.5) +
#     scale_y_continuous(labels = scales::comma) +
#     scale_x_date(date_labels = "%b %d") +
#     labs(x = NULL, y = "steps") +
#     theme(plot.title = element_text(hjust = 0.5)) +
#     dash_theme()
#   
#   ggplotly(p) %>% 
#     layout(hoverlabel = list(bgcolor = clr$bg),
#            margin = list(l = 50, r = 20, t = 50, b = 40))
# })
```

### 7. Sleep Stage Breakdown

Daily breakdown of sleep stages (Deep, REM, Light) in total minutes. Shows sleep quality patterns and helps identify factors affecting sleep architecture.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# Aggregate sleep stages per night
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  sleep_summary <- sleep_data %>%
    group_by(dateOfSleep, sleep_stage) %>%
    summarise(minutes = n(), .groups = "drop") %>%
    filter(sleep_stage %in% c("deep", "rem", "light")) %>%
    mutate(
      sleep_stage = recode(sleep_stage,
                          deep = "Deep",
                          rem = "REM",
                          light = "Light"),
      dateOfSleep = as.Date(dateOfSleep)
    )
  
  # Optional: Filter to specific date range if needed
  # sleep_summary <- sleep_summary %>%
  #   filter(dateOfSleep >= as.Date("2026-05-28"), dateOfSleep <= as.Date("2026-06-08"))
}

# ===== CHART CODE =====
if (exists("sleep_summary") && !is.null(sleep_summary) && nrow(sleep_summary) > 0) {
  sleep_plot <- ggplot(sleep_summary, aes(x = dateOfSleep, y = minutes, fill = sleep_stage)) +
    geom_col(width = 0.7, alpha = 0.9) +
    scale_fill_manual(values = c(Deep = clr$deep, REM = clr$rem, Light = clr$light)) +
    scale_x_date(date_labels = "%b %d") +
    labs(x = NULL, y = "minutes") +
    # Remove title from ggplot since we'll set it in Plotly
    # labs(title = NULL, x = NULL, y = "minutes") +
    dash_theme()
  
  # Convert to interactive plotly
  ggplotly(sleep_plot, tooltip = c("x", "y", "fill")) %>%
    layout(
      hoverlabel = list(bgcolor = clr$bg),  # Remove quotes!
      title = list(text = "Daily Sleep States", x = 0.5),
      margin = list(l = 50, r = 20, t = 50, b = 40),
      legend = list(
        orientation = "h",           # Horizontal legend
        yanchor = "bottom",          # Anchor at bottom
        y = -0.15,                   # Position below chart (adjust as needed)
        xanchor = "center",          # Center horizontally
        x = 0.5                     # Center position
        #bgcolor = "rgba(255,255,255,0.8)"  # Semi-transparent background
      )
    ) %>%
    # ADD THIS: Explicitly set colors in Plotly
    style(
      marker = list(
        color = ~ifelse(sleep_stage == "Deep", clr$deep,
                 ifelse(sleep_stage == "REM", clr$rem,
                 clr$light))
      )
    )
} else {
  create_empty_plot("No sleep data available")
}

# ===== FOR APP.R: Add to UI =====
# shinyfullscreen::fullscreen_this(
#   plotlyOutput("plot_sleep"),
#   click_to_fullscreen = TRUE
# )
#
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$plot_sleep <- renderPlotly({
#   req(sleep_data())
#   
#   df <- sleep_data()
#   if (is.null(df) || nrow(df) == 0) {
#     return(create_empty_plot("No sleep data available"))
#   }
#   
#   # Aggregate sleep stages per night
#   sleep_summary <- df %>%
#     group_by(dateOfSleep, sleep_stage) %>%
#     summarise(minutes = n(), .groups = "drop") %>%
#     filter(sleep_stage %in% c("deep", "rem", "light")) %>%
#     mutate(sleep_stage = recode(sleep_stage,
#                                 deep = "Deep",
#                                 rem = "REM",
#                                 light = "Light"))
#   
#   if (nrow(sleep_summary) == 0) {
#     return(create_empty_plot("No sleep stage data available"))
#   }
#   
#   p <- ggplot(sleep_summary, aes(x = as.Date(dateOfSleep), y = minutes, fill = sleep_stage)) +
#     geom_col(width = 0.7, alpha = 0.9) +
#     scale_fill_manual(values = c(Deep = clr$deep, REM = clr$rem, Light = clr$light)) +
#     scale_x_date(date_labels = "%b %d") +
#     labs(x = NULL, y = "minutes") +
#     dash_theme()
#   
#   ggplotly(p) %>% 
#     layout(
#       hoverlabel = list(bgcolor = clr$bg),
#       title = list(text = "Daily Sleep States", x = 0.5),
#       margin = list(l = 50, r = 20, t = 50, b = 40),
#       legend = list(
#         orientation = "h",
#         yanchor = "bottom",
#         y = -0.15,
#         xanchor = "center",
#         x = 0.5,
#         bgcolor = "rgba(255,255,255,0.8)"
#       )
#     ) %>%
#     # ADD THIS: Explicitly set colors in Plotly
#     style(
#       marker = list(
#         color = ~ifelse(sleep_stage == "Deep", clr$deep,
#                  ifelse(sleep_stage == "REM", clr$rem,
#                  clr$light))
#       )
#     )
# })
```

### 8. Sleep Stage Distribution

Overall percentages of time in each stage (Deep, REM, Light, Wake) across all dates combined

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== SLEEP STAGE DISTRIBUTION (DONUT) =====
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  stage_dist <- sleep_data %>%
    filter(sleep_stage %in% c("deep", "rem", "light", "wake")) %>%
    group_by(sleep_stage) %>%
    summarise(minutes = n(), .groups = "drop") %>%
    mutate(
      sleep_stage = recode(sleep_stage,
                          deep = "Deep",
                          rem = "REM",
                          light = "Light",
                          wake = "Wake"),
      percentage = round(minutes / sum(minutes) * 100, 1)
    )
  
  plot_ly(
    data = stage_dist,
    labels = ~sleep_stage,
    values = ~minutes,
    type = "pie",
    hole = 0.6,
    textinfo = "label+percent",
    hoverinfo = "label+value+percent",
    hoverlabel = list(bgcolor = clr$bg),
    marker = list(
      colors = c(Deep = clr$deep, REM = clr$rem, Light = clr$light, Wake = clr$wake)
    )
  ) %>%
    layout(
      title = list(text = "Sleep Stage Distribution", x = 0.5),
      margin = list(l = 20, r = 20, t = 50, b = 20),
      legend = list(
        orientation = "h",
        yanchor = "bottom",
        y = -0.2,
        xanchor = "center",
        x = 0.5
      ),
      showlegend = TRUE
    )
} else {
  create_empty_plot("No sleep data available")
}
```

## Heart Rate Tab

### 14. HR Time Series w/Overlay

Raw heart rate values (thin line) with a LOESS smooth trend (thick line) to reveal daily patterns and overall trend. Helps identify resting HR trends, exercise intensity periods, and potential recovery patterns.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# For Rmd: use full dataset
# For App.R: hr_data() is already filtered by date and participant
chart_data <- hr_data %>%
  filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08"))

# ===== CHART CODE =====
# Create the ggplot object
hr_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = heart_rate_avg)) +
  # Raw data line - thin, semi-transparent
  geom_line(color = clr$hr, linewidth = 0.3, alpha = 0.5) +
  # LOESS smooth trend - thicker, solid
  geom_smooth(method = "loess", span = 0.1, se = FALSE, 
              color = clr$hr, linewidth = .5, alpha = 0.9) +
  # Labels with clear descriptions
  labs(
    # title = "Heart Rate Over Time",
    x = "Date and Time",
    y = "Heart Rate (beats per minute)"
  ) +
  # Format x-axis dates
  scale_x_datetime(
    date_labels = "%b %d, %H:%M",
    date_breaks = "12 hours"
  ) +
  # Format y-axis
  scale_y_continuous(
    limits = c(55, 150),
    breaks = seq(40, 150, by = 20),
    labels = scales::label_number(suffix = " bpm")
  ) +
  dash_theme() +
  theme(
    axis.text.x = element_text(size = 8),  # Makes X-axis tick labels smaller
    axis.text.y = element_text(size = 8),  # Makes Y-axis tick labels smaller
    axis.title.x = element_text(size = 9), # Optional: Makes X-axis title smaller
    axis.title.y = element_text(size = 9)  # Optional: Makes Y-axis title smaller
  )

# Convert to interactive plotly
ggplotly(hr_timeseries_plot, tooltip = c("x", "y")) %>%
  layout(
    xaxis = list(tickangle = -45),
    title = list(text = "Heart Rate Over Time", x = 0.5),
    margin = list(l = 50, r = 20, t = 50, b = 40),
    hoverlabel = list(bgcolor = clr$bg, font = list(size = 10)),
    legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "right", x = 1)
  )

# ===== FOR APP.R: Add to UI =====
# To use shinyfullscreen package to allow shiny app charts to full screen,
# we added library(shinyfullscreen) to app.R and we need to wrap the plotlyOutput
# in the UI section like this:
#
# shinyfullscreen::fullscreen_this(
#         plotlyOutput("hr_timeseries"),
#         click_to_fullscreen = TRUE
# )
#
# We should do this for every chart :)
#
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hr_timeseries <- renderPlotly({
#   req(hr_data())
#   
#   # Filter out invalid HR values
#   chart_data <- hr_data() %>%
#     filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220)
#   
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No heart rate data available for selected filters"))
#   }
#   
#   hr_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = heart_rate_avg)) +
#     geom_line(color = clr$hr, linewidth = 0.3, alpha = 0.5) +
#     geom_smooth(method = "loess", span = 0.1, se = FALSE, 
#                 color = clr$hr, linewidth = 0.5, alpha = 0.9) +
#     labs(x = "Date and Time", y = "Heart Rate (beats per minute)") +
#     scale_x_datetime(date_labels = "%b %d, %H:%M", date_breaks = "12 hours") +
#     scale_y_continuous(limits = c(55, 150), breaks = seq(40, 150, by = 20)) +
#     dash_theme() +
#     theme(
#           axis.text.x = element_text(size = 8),  # Makes X-axis tick labels smaller
#           axis.text.y = element_text(size = 8),  # Makes Y-axis tick labels smaller
#           axis.title.x = element_text(size = 9), # Optional: Makes X-axis title smaller
#           axis.title.y = element_text(size = 9)  # Optional: Makes Y-axis title smaller
#     )
#   
#   ggplotly(hr_timeseries_plot, tooltip = c("x", "y")) %>%
#     layout(
#         xaxis = list(tickangle = -45),
#         hoverlabel = list(bgcolor = clr$bg, font = list(size = 10)),
#         title = list(text = "Heart Rate Over Time", x = 0.5),
#         margin = list(l = 50, r = 20, t = 50, b = 40),
#         legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "right", x = 1)
# })
```

### 15. Heart Rate by Hour

Average heart rate for each hour of the day (e.g., 8 AM average, 9 AM average) across the selected date range. Reveals daily circadian patterns, typical resting HR during sleep, and peak activity hours.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# Extract hour from datetime, then calculate average HR per hour
chart_data <- hr_data %>%
  filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08")) %>%
  mutate(
    hour_of_day = hour(datetime),
    hour_label = sprintf("%02d:00", hour_of_day)
  ) %>%
  group_by(hour_of_day, hour_label) %>%
  summarise(
    avg_heart_rate = mean(heart_rate_avg, na.rm = TRUE),
    sd_heart_rate = sd(heart_rate_avg, na.rm = TRUE),
    .groups = "drop"
  )

# ===== CHART CODE =====
hr_by_hour_plot <- ggplot(chart_data, aes(x = hour_of_day, y = avg_heart_rate)) +
  # Column chart with error bars (standard deviation)
  geom_col(fill = clr$hr, width = 0.7, alpha = 0.8) +
  geom_errorbar(aes(ymin = avg_heart_rate - sd_heart_rate, 
                    ymax = avg_heart_rate + sd_heart_rate),
                width = 0.3, color = clr$error_bar, linewidth = 0.4) +
  # Smooth trend line to show daily pattern
  geom_smooth(method = "loess", se = FALSE, color = clr$max, linewidth = 0.8, linetype = "dashed") +
  # Labels
  labs(
    # title = "Average Heart Rate by Hour of Day",
    x = "Hour of Day",
    y = "Average Heart Rate (beats per minute)"
  ) +
  # X-axis: show every 2 hours
  scale_x_continuous(
    breaks = seq(0, 23, by = 2),
    labels = sprintf("%02d:00", seq(0, 23, by = 2))
  ) +
  scale_y_continuous(limits = c(55, 110), breaks = seq(55, 110, by = 10)) +
  dash_theme() +
  theme(panel.grid.major.x = element_blank())

# Convert to interactive plotly
ggplotly(hr_by_hour_plot, tooltip = c("x", "y", "ymin", "ymax")) %>%
  layout(
    hoverlabel = list(bgcolor = clr$bg),
    title = list(text = "Average Heart RateBy Hour", x = 0.5),
    margin = list(l = 50, r = 20, t = 50, b = 40),
    legend = list(orientation = "h", yanchor = "bottom", y = 1.02)
  )

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hr_by_hour <- renderPlotly({
#   req(hr_data())
#   
#   chart_data <- hr_data() %>%
#     filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220) %>%
#     mutate(
#       hour_of_day = hour(datetime),
#       hour_label = sprintf("%02d:00", hour_of_day)
#     ) %>%
#     group_by(hour_of_day, hour_label) %>%
#     summarise(
#       avg_heart_rate = mean(heart_rate_avg, na.rm = TRUE),
#       sd_heart_rate = sd(heart_rate_avg, na.rm = TRUE),
#       .groups = "drop"
#     )
#   
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No heart rate data available for selected filters"))
#   }
#   
#   hr_by_hour_plot <- ggplot(chart_data, aes(x = hour_of_day, y = avg_heart_rate)) +
#     geom_col(fill = clr$hr, width = 0.7, alpha = 0.8) +
#     geom_errorbar(aes(ymin = avg_heart_rate - sd_heart_rate, 
#                       ymax = avg_heart_rate + sd_heart_rate),
#                   width = 0.3, color = clr$error_bar, linewidth = 0.4) +
#     geom_smooth(method = "loess", se = FALSE, color = clr$target_line, linewidth = 0.8, linetype = "dashed") +
#     labs(x = "Hour of Day", y = "Average Heart Rate (beats per minute)") +
#     scale_x_continuous(breaks = seq(0, 23, by = 2), labels = sprintf("%02d:00", seq(0, 23, by = 2))) +
#     scale_y_continuous(limits = c(55, 110), breaks = seq(55, 110, by = 10)) +
#     dash_theme() +
#     theme(panel.grid.major.x = element_blank())
#   
#   ggplotly(hr_by_hour_plot, tooltip = c("x", "y", "ymin", "ymax")) %>%
#     layout(
#       hoverlabel = list(bgcolor = clr$bg),
#       title = list(text = "Average Heart RateBy Hour", x = 0.5),
#       margin = list(l = 50, r = 20, t = 50, b = 40),
#       legend = list(orientation = "h", yanchor = "bottom", y = 1.02)
#     )
# })
```

### 16. Daily Min/Avg/Max Heart Rate

For each day, three lines: minimum HR, average HR, and maximum HR. Shows daily heart rate variability, identifies high-stress days, and reveals recovery patterns (lower resting HR indicates good recovery).

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
chart_data <- hr_data %>%
  filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08")) %>%
  mutate(date_only = as.Date(datetime)) %>%
  group_by(date_only) %>%
  summarise(
    min_hr = min(heart_rate_avg, na.rm = TRUE),
    avg_hr = mean(heart_rate_avg, na.rm = TRUE),
    max_hr = max(heart_rate_avg, na.rm = TRUE),
    .groups = "drop"
  )

# ===== CHART CODE =====
plot_ly() %>%
  add_trace(
    data = chart_data,
    x = ~date_only, y = ~min_hr,
    type = "scatter", mode = "lines+markers",
    name = "Minimum HR",
    line   = list(color = clr$min, width = 0.5),
    marker = list(color = clr$min, size = 6, opacity = 0.7)
  ) %>%
  add_trace(
    data = chart_data,
    x = ~date_only, y = ~avg_hr,
    type = "scatter", mode = "lines+markers",
    name = "Average HR",
    line   = list(color = clr$avg, width = 0.5),
    marker = list(color = clr$avg, size = 6, opacity = 0.7)
  ) %>%
  add_trace(
    data = chart_data,
    x = ~date_only, y = ~max_hr,
    type = "scatter", mode = "lines+markers",
    name = "Maximum HR",
    line   = list(color = clr$max, width = 0.5),
    marker = list(color = clr$max, size = 6, opacity = 0.7)
  ) %>%
  layout(
    title      = list(text = "Daily Heart Rate Statistics", x = 0.5),
    xaxis      = list(title = "Date", tickformat = "%b %d", dtick = 86400000),
    yaxis      = list(title = "Heart Rate (beats per minute)", range = c(40, 160), tickvals = seq(40, 160, by = 20)),
    legend     = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2),
    hoverlabel = list(bgcolor = clr$bg),
    margin     = list(l = 50, r = 20, t = 50, b = 60)
  )

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code

# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hr_daily_stats <- renderPlotly({
#   req(hr_data())
#
#   chart_data <- hr_data() %>%
#     filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220) %>%
#     mutate(date_only = as.Date(datetime)) %>%
#     group_by(date_only) %>%
#     summarise(
#       min_hr = min(heart_rate_avg, na.rm = TRUE),
#       avg_hr = mean(heart_rate_avg, na.rm = TRUE),
#       max_hr = max(heart_rate_avg, na.rm = TRUE),
#       .groups = "drop"
#     )
#
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No heart rate data available for selected filters"))
#   }
#
#   plot_ly() %>%
#     add_trace(
#       data = chart_data,
#       x = ~date_only, y = ~min_hr,
#       type = "scatter", mode = "lines+markers",
#       name = "Minimum HR",
#       line   = list(color = clr$min, width = 0.5),
#       marker = list(color = clr$min, size = 6, opacity = 0.7)
#     ) %>%
#     add_trace(
#       data = chart_data,
#       x = ~date_only, y = ~avg_hr,
#       type = "scatter", mode = "lines+markers",
#       name = "Average HR",
#       line   = list(color = clr$avg, width = 0.5),
#       marker = list(color = clr$avg, size = 6, opacity = 0.7)
#     ) %>%
#     add_trace(
#       data = chart_data,
#       x = ~date_only, y = ~max_hr,
#       type = "scatter", mode = "lines+markers",
#       name = "Maximum HR",
#       line   = list(color = clr$max, width = 0.5),
#       marker = list(color = clr$max, size = 6, opacity = 0.7)
#     ) %>%
#     layout(
#       xaxis      = list(title = "Date", tickformat = "%b %d", dtick = 86400000),
#       yaxis      = list(title = "Heart Rate (beats per minute)", range = c(40, 160), tickvals = seq(40, 160, by = 20)),
#       legend     = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2),
#       hoverlabel = list(bgcolor = clr$bg),
#       margin     = list(l = 50, r = 20, t = 50, b = 60)
#     )
# })
```

### 17. Activity Zone Minutes

Daily breakdown of minutes spent in Fat Burn, Cardio, and Peak heart rate zones.
Shows workout intensity distribution. Helps users understand if they're meeting weekly zone minute goals (typically 150+ minutes of moderate-to-vigorous activity).

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION ===== #
chart_data <- zone_data %>%
  filter(!is.na(datetime)) %>%
  mutate(date_only = as.Date(datetime)) %>%
  group_by(date_only) %>%
  summarise(
    fat_burn = sum(fat_burn_minutes, na.rm = TRUE),
    cardio   = sum(cardio_minutes,   na.rm = TRUE),
    peak     = sum(peak_minutes,     na.rm = TRUE),
    total_active = fat_burn + cardio + peak,
    .groups = "drop"
  ) %>%
  filter(date_only >= as.Date("2026-05-28"), date_only <= as.Date("2026-06-08"))

# ===== CHART CODE ===== #
plot_ly() %>%
  add_bars(
    data = chart_data,
    x = ~date_only, y = ~fat_burn,
    name = "Fat Burn Zone",
    marker = list(color = clr$fat_burn, opacity = 0.9)
  ) %>%
  add_bars(
    data = chart_data,
    x = ~date_only, y = ~cardio,
    name = "Cardio Zone",
    marker = list(color = clr$cardio, opacity = 0.9)
  ) %>%
  add_bars(
    data = chart_data,
    x = ~date_only, y = ~peak,
    name = "Peak Zone",
    marker = list(color = clr$peak, opacity = 0.9)
  ) %>%
  add_annotations(
    data = filter(chart_data, total_active > 0),
    x = ~date_only, y = ~total_active,
    text = ~total_active,
    showarrow = FALSE,
    yshift = 8,
    font = list(color = clr$error_bar, size = 10)
  ) %>%
  add_segments(
    x = min(chart_data$date_only), xend = max(chart_data$date_only),
    y = 21, yend = 21,
    line = list(color = clr$grid_line, width = 0.5, dash = "dash"),
    showlegend = FALSE
  ) %>%
  add_annotations(
    x = min(chart_data$date_only), y = 23,
    text = "Daily target (150 min/week)",
    showarrow = FALSE,
    xanchor = "left",
    font = list(color = clr$text_secondary, size = 9)
  ) %>%
  layout(
    barmode   = "stack",
    autosize  = TRUE,
    xaxis     = list(title = "Date", tickformat = "%b %d", dtick = 86400000),
    yaxis     = list(title = "Minutes", range = c(0, max(chart_data$total_active, na.rm = TRUE) + 15), tickvals = seq(0, 100, by = 20)),
    legend    = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2),
    hoverlabel = list(bgcolor = clr$bg),
    title      = list(text = "Activity Zone Minutes", x = 0.5),
    margin    = list(l = 50, r = 20, t = 50, b = 60)
  )

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code

# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hr_zone_minutes <- renderPlotly({
#   req(zone_data())
#
#   chart_data <- zone_data() %>%
#     filter(!is.na(datetime)) %>%
#     mutate(date_only = as.Date(datetime)) %>%
#     group_by(date_only) %>%
#     summarise(
#       fat_burn = sum(fat_burn_minutes, na.rm = TRUE),
#       cardio   = sum(cardio_minutes,   na.rm = TRUE),
#       peak     = sum(peak_minutes,     na.rm = TRUE),
#       total_active = fat_burn + cardio + peak,
#       .groups = "drop"
#     )
#
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No heart rate zone data available for selected filters"))
#   }
#
#   plot_ly() %>%
#     add_bars(
#       data = chart_data,
#       x = ~date_only, y = ~fat_burn,
#       name = "Fat Burn Zone",
#       marker = list(color = clr$fat_burn, opacity = 0.9)
#     ) %>%
#     add_bars(
#       data = chart_data,
#       x = ~date_only, y = ~cardio,
#       name = "Cardio Zone",
#       marker = list(color = clr$cardio, opacity = 0.9)
#     ) %>%
#     add_bars(
#       data = chart_data,
#       x = ~date_only, y = ~peak,
#       name = "Peak Zone",
#       marker = list(color = clr$peak, opacity = 0.9)
#     ) %>%
#     add_annotations(
#       data = filter(chart_data, total_active > 0),
#       x = ~date_only, y = ~total_active,
#       text = ~total_active,
#       showarrow = FALSE,
#       yshift = 8,
#       font = list(color = clr$error_bar, size = 10)
#     ) %>%
#     add_segments(
#       x = min(chart_data$date_only), xend = max(chart_data$date_only),
#       y = 21, yend = 21,
#       line = list(color = clr$grid_line, width = 0.5, dash = "dash"),
#       showlegend = FALSE
#     ) %>%
#     add_annotations(
#       x = min(chart_data$date_only), y = 23,
#       text = "Daily target (150 min/week)",
#       showarrow = FALSE,
#       xanchor = "left",
#       font = list(color = clr$grid_line, size = 9)
#     ) %>%
#     layout(
#       barmode    = "stack",
#       autosize   = TRUE,
#       xaxis      = list(title = "Date", tickformat = "%b %d", dtick = 86400000),
#       yaxis      = list(title = "Minutes", range = c(0, max(chart_data$total_active, na.rm = TRUE) + 15), tickvals = seq(0, 100, by = 20)),
#       legend     = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2),
#       hoverlabel = list(bgcolor = clr$bg),
#       margin     = list(l = 50, r = 20, t = 20, b = 60)
#     )
# })
```

## 18. Admin: HRV Time Series

Heart Rate Variability RMSSD values over time. Higher HRV indicates better recovery and parasympathetic nervous system activation. Tracks recovery status. Low HRV may indicate stress, fatigue, or over-training. High HRV (relative to baseline) suggests good recovery.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# HRV data is less frequent (typically every 5 minutes during sleep)
chart_data <- hrv_data %>%
  filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08"))

# Calculate baseline (rolling average) for comparison
chart_data <- chart_data %>%
  arrange(datetime) %>%
  mutate(
    rolling_avg = zoo::rollapply(rmssd_ms, width = 10, FUN = mean, fill = NA, align = "center")
  )

# ===== CHART CODE =====
hrv_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = rmssd_ms)) +
  # Raw HRV points
  geom_point(color = clr$hr, alpha = 0.4, size = 1) +
  # LOESS smooth trend
  geom_smooth(method = "loess", se = TRUE, fill = clr$hr, 
              color = clr$hr, linewidth = 1) +
  # Rolling average line (optional overlay)
  geom_line(aes(y = rolling_avg), color = clr$text_primary, linewidth = 0.5, alpha = 0.6, na.rm = TRUE) +
  # Reference line for typical HRV baseline (adjust based on participant)
  geom_hline(yintercept = 20, linetype = "dashed", color = clr$text_secondary, linewidth = 0.4, alpha = 0.7) +
  # Annotations
  annotate("text", x = min(chart_data$datetime), y = 22, 
           label = "Typical baseline", hjust = 0, size = 3, color = clr$text_secondary) +
  # Labels
  labs(
    title = "Heart Rate Variability (HRV) Over Time",
    x = "Date and Time",
    y = "RMSSD (milliseconds)",
    caption = "Higher HRV indicates better recovery | Lower HRV may indicate stress or fatigue"
  ) +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "1 day") +
  scale_y_continuous(limits = c(0, 60), breaks = seq(0, 60, by = 10)) +
  dash_theme()

# Convert to interactive plotly
ggplotly(hrv_timeseries_plot, tooltip = c("x", "y")) %>%
  layout(
    title      = list(text = "Activity Zone Minutes", x = 0.5),
    margin    = list(l = 50, r = 20, t = 50, b = 60),
    hoverlabel = list(bgcolor = clr$bg),
    annotations = list(
      x = 0, y = -0.15, xref = "paper", yref = "paper",
      text = "Higher HRV = better recovery",
      showarrow = FALSE,
      font = list(size = 10, color = clr$text_secondary)
    )
  )

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hrv_chart <- renderPlotly({
#   req(hrv_data())
#   
#   chart_data <- hrv_data() %>%
#     filter(!is.na(datetime), rmssd_ms > 0, rmssd_ms < 200)
#   
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No HRV data available for selected filters"))
#   }
#   
#   # Calculate rolling average (need zoo package)
#   # library(zoo) - add to app.R
#   chart_data <- chart_data %>%
#     arrange(datetime) %>%
#     mutate(rolling_avg = zoo::rollapply(rmssd_ms, width = min(10, n()), FUN = mean, fill = NA, align = "center"))
#   
#   hrv_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = rmssd_ms)) +
#     geom_point(color = clr$hr, alpha = 0.4, size = 1) +
#     geom_smooth(method = "loess", se = TRUE, fill = "#E24B4A20", color = clr$hr, linewidth = 1) +
#     geom_line(aes(y = rolling_avg), color = "#1A1A2E", linewidth = 0.5, alpha = 0.6, na.rm = TRUE) +
#     geom_hline(yintercept = 20, linetype = "dashed", color = "#9CA3AF", linewidth = 0.4) +
#     labs(x = "Date and Time", y = "RMSSD (milliseconds)", 
#          caption = "Higher HRV indicates better recovery | Lower HRV may indicate stress or fatigue") +
#     scale_x_datetime(date_labels = "%b %d", date_breaks = "1 day") +
#     scale_y_continuous(limits = c(0, 60), breaks = seq(0, 60, by = 10)) +
#     dash_theme()
#   
#   ggplotly(hrv_timeseries_plot, tooltip = c("x", "y")) %>%
#     layout(hoverlabel = list(bgcolor = "white"))
# })
```


## Sleep Tab

### 28. Hypnogram

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION ===== #
target_date <- as.Date("2026-06-01")

# Identify all sleep sessions and find the primary (longest) one
sleep_sessions <- sleep_minute %>%
  filter(dateOfSleep == target_date) %>%
  group_by(logId) %>%
  summarise(
    session_start = min(as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")),
    session_end = max(as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")),
    duration_minutes = n(),
    .groups = "drop"
  ) %>%
  mutate(
    session_label = paste(format(session_start, "%H:%M"), "-", format(session_end, "%H:%M")),
    session_choice = paste(session_label, "(", duration_minutes, "min)")
  )

# For markdown, use the primary session (longest)
primary_session_id <- sleep_sessions$logId[which.max(sleep_sessions$duration_minutes)]

# Prepare hypnogram data for primary session
hypnogram_data <- sleep_minute %>%
  filter(dateOfSleep == target_date) %>%
  filter(logId == primary_session_id) %>%
  filter(sleep_stage %in% c("wake", "light", "deep", "rem", "asleep")) %>%
  mutate(
    datetime_utc = as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC"),
    time_num = hour(datetime_utc) + minute(datetime_utc) / 60,
    stage_numeric = case_when(
      sleep_stage == "wake" ~ 4,
      sleep_stage == "rem" ~ 3,
      sleep_stage == "light" ~ 2,
      sleep_stage == "deep" ~ 1,
      sleep_stage == "asleep" ~ 2
    ),
    stage_label = case_when(
      sleep_stage == "wake" ~ "Wake",
      sleep_stage == "rem" ~ "REM",
      sleep_stage == "light" ~ "Light",
      sleep_stage == "deep" ~ "Deep",
      sleep_stage == "asleep" ~ "Asleep"
    )
  )

# ===== PLOTLY CHART CODE ===== #
# Create the plot using clr palette
hypnogram_plot <- plot_ly() %>%
  # Add line
  add_lines(
    data = hypnogram_data,
    x = ~time_num,
    y = ~stage_numeric,
    line = list(color = clr$text_primary, width = 2),
    name = "Sleep Stage",
    showlegend = FALSE,
    hoverinfo = "skip"
  ) %>%
  # Add points with colors from clr
  add_markers(
    data = hypnogram_data,
    x = ~time_num,
    y = ~stage_numeric,
    color = ~stage_label,
    colors = c(
      "Wake" = clr$wake,
      "REM" = clr$rem,
      "Light" = clr$light,
      "Deep" = clr$deep,
      "Asleep" = clr$text_secondary
    ),
    marker = list(size = 10, opacity = 0.7),
    text = ~paste(
      "Time:", sprintf("%02d:%02d", floor(time_num), round((time_num - floor(time_num)) * 60)),
      "<br>Stage:", stage_label
    ),
    hoverinfo = "text",
    showlegend = TRUE
  ) %>%
  # Layout configuration
  layout(
    title = list(
      text = paste("Sleep Hypnogram -", format(target_date, "%B %d, %Y")),
      x = 0.5,
      xanchor = "center",
      font = list(size = 16, family = "Arial", color = clr$text_primary)
    ),
    xaxis = list(
      title = "Time",
      tickmode = "array",
      tickvals = seq(0, 24, 2),
      ticktext = c("12 AM", "2 AM", "4 AM", "6 AM", "8 AM", "10 AM", 
                   "12 PM", "2 PM", "4 PM", "6 PM", "8 PM", "10 PM", "12 AM"),
      range = c(0, 24),
      gridcolor = clr$target_line,
      gridwidth = 0.5,
      zeroline = FALSE,
      showline = TRUE,
      linecolor = "gray",
      linewidth = 1
    ),
    yaxis = list(
      title = "Sleep Stage",
      tickmode = "array",
      tickvals = c(4, 3, 2, 1),
      ticktext = c("Wake", "REM", "Light", "Deep"),
      range = c(0.5, 4.5),
      autorange = FALSE,
      gridcolor = clr$target_line,
      gridwidth = 0.5,
      zeroline = FALSE,
      showline = TRUE,
      linecolor = "gray",
      linewidth = 1
    ),
    legend = list(
      orientation = "h",
      yanchor = "bottom",
      y = -0.3,
      xanchor = "center",
      x = 0.5,
      title = list(text = "Stage"),
      font = list(size = 11, color = clr$text_primary)
    ),
    hoverlabel = list(
      bgcolor = clr$bg,
      font = list(color = clr$text_primary)
    ),
    margin = list(
      l = 60,
      r = 40,
      t = 80,
      b = 80
    ),
    plot_bgcolor = clr$bg,
    paper_bgcolor = clr$bg
  ) %>%
  # Add subtitle if multiple sessions
  config(displayModeBar = TRUE)

# Display the plot
hypnogram_plot

# ===== FOR APP.R: Add to UI ===== #
# In UI, add:
# selectInput("sleep_session", "Select Sleep Session", choices = NULL)
#
# shinyfullscreen::fullscreen_this(
#   plotlyOutput("hypnogram_chart"),
#   click_to_fullscreen = TRUE
# )

# ===== FOR APP.R: Wrap in renderPlotly ===== #
# output$hypnogram_chart <- renderPlotly({
#   req(sleep_data(), input$hypnogram_date)
#   
#   target_date_shiny <- as.Date(input$hypnogram_date)
#   
#   # Identify all sleep sessions and create dropdown choices
#   sleep_sessions_shiny <- sleep_data() %>%
#     filter(dateOfSleep == target_date_shiny) %>%
#     group_by(logId) %>%
#     summarise(
#       session_start = min(as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")),
#       session_end = max(as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")),
#       duration_minutes = n(),
#       .groups = "drop"
#     ) %>%
#     mutate(
#       session_label = paste(format(session_start, "%H:%M"), "-", format(session_end, "%H:%M")),
#       session_choice = paste(session_label, "(", duration_minutes, "min)")
#     )
#   
#   # Update dropdown choices
#   updateSelectInput(session, "sleep_session", 
#                     choices = setNames(sleep_sessions_shiny$logId, sleep_sessions_shiny$session_choice),
#                     selected = sleep_sessions_shiny$logId[1])
#   
#   # Get selected session
#   selected_session <- input$sleep_session
#   
#   # If nothing selected yet, use first session
#   if(is.null(selected_session)) {
#     selected_session <- sleep_sessions_shiny$logId[1]
#   }
#   
#   # Prepare hypnogram data for selected session
#   hypnogram_data_shiny <- sleep_data() %>%
#     filter(dateOfSleep == target_date_shiny) %>%
#     filter(logId == selected_session) %>%
#     filter(sleep_stage %in% c("wake", "light", "deep", "rem", "asleep")) %>%
#     mutate(
#       datetime_utc = as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC"),
#       time_num = hour(datetime_utc) + minute(datetime_utc) / 60,
#       stage_numeric = case_when(
#         sleep_stage == "wake" ~ 4,
#         sleep_stage == "rem" ~ 3,
#         sleep_stage == "light" ~ 2,
#         sleep_stage == "deep" ~ 1,
#         sleep_stage == "asleep" ~ 2
#       ),
#       stage_label = case_when(
#         sleep_stage == "wake" ~ "Wake",
#         sleep_stage == "rem" ~ "REM",
#         sleep_stage == "light" ~ "Light",
#         sleep_stage == "deep" ~ "Deep",
#         sleep_stage == "asleep" ~ "Asleep"
#       )
#     )
#   
#   if (nrow(hypnogram_data_shiny) == 0) {
#     return(create_empty_plot(paste("No sleep stage data for", target_date_shiny)))
#   }
#   
#   # Get selected session label for subtitle
#   selected_label <- sleep_sessions_shiny %>%
#     filter(logId == selected_session) %>%
#     pull(session_label)
#   
#   # Create plotly chart using clr
#   plot_ly() %>%
#     add_lines(
#       data = hypnogram_data_shiny,
#       x = ~time_num,
#       y = ~stage_numeric,
#       line = list(color = clr$text_primary, width = 2),
#       name = "Sleep Stage",
#       showlegend = FALSE,
#       hoverinfo = "skip"
#     ) %>%
#     add_markers(
#       data = hypnogram_data_shiny,
#       x = ~time_num,
#       y = ~stage_numeric,
#       color = ~stage_label,
#       colors = c(
#         "Wake" = clr$wake,
#         "REM" = clr$rem,
#         "Light" = clr$light,
#         "Deep" = clr$deep,
#         "Asleep" = clr$text_secondary
#       ),
#       marker = list(size = 10, opacity = 0.7),
#       text = ~paste(
#         "Time:", sprintf("%02d:%02d", floor(time_num), round((time_num - floor(time_num)) * 60)),
#         "<br>Stage:", stage_label
#       ),
#       hoverinfo = "text",
#       showlegend = TRUE
#     ) %>%
#     layout(
#       title = list(
#         text = paste("Sleep Hypnogram -", format(target_date_shiny, "%B %d, %Y"),
#                      "<br><sup>Session:", selected_label, "</sup>"),
#         x = 0.5,
#         xanchor = "center",
#         font = list(size = 16, family = "Arial", color = clr$text_primary)
#       ),
#       xaxis = list(
#         title = "Time",
#         tickmode = "array",
#         tickvals = seq(0, 24, 2),
#         ticktext = c("12 AM", "2 AM", "4 AM", "6 AM", "8 AM", "10 AM", 
#                      "12 PM", "2 PM", "4 PM", "6 PM", "8 PM", "10 PM", "12 AM"),
#         range = c(0, 24),
#         gridcolor = clr$target_line,
#         gridwidth = 0.5,
#         zeroline = FALSE,
#         showline = TRUE,
#         linecolor = "gray",
#         linewidth = 1
#       ),
#       yaxis = list(
#         title = "Sleep Stage",
#         tickmode = "array",
#         tickvals = c(4, 3, 2, 1),
#         ticktext = c("Wake", "REM", "Light", "Deep"),
#         range = c(0.5, 4.5),
#         autorange = FALSE,
#         gridcolor = clr$target_line,
#         gridwidth = 0.5,
#         zeroline = FALSE,
#         showline = TRUE,
#         linecolor = "gray",
#         linewidth = 1
#       ),
#       legend = list(
#         orientation = "h",
#         yanchor = "bottom",
#         y = -0.3,
#         xanchor = "center",
#         x = 0.5,
#         title = list(text = "Stage"),
#         font = list(size = 11, color = clr$text_primary)
#       ),
#       hoverlabel = list(
#         bgcolor = clr$bg,
#         font = list(color = clr$text_primary)
#       ),
#       margin = list(
#         l = 60,
#         r = 40,
#         t = 80,
#         b = 80
#       ),
#       plot_bgcolor = clr$bg,
#       paper_bgcolor = clr$bg
#     ) %>%
#     config(displayModeBar = TRUE)
# })
```


### 29. Sleep Duration per Night

Total duration of how much sleep was gotten per night over time, all staged summed.How many hours am I sleeping each night?

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== SLEEP DURATION PER NIGHT =====
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  sleep_duration <- sleep_data %>%
    filter(sleep_stage %in% c("deep", "rem", "light", "wake")) %>%
    group_by(dateOfSleep) %>%
    summarise(total_minutes = n(), .groups = "drop") %>%
    mutate(dateOfSleep = as.Date(dateOfSleep))
  
  plot_ly(
    data = sleep_duration,
    x = ~dateOfSleep,
    y = ~total_minutes,
    type = "bar",
    marker = list(color = clr$deep, opacity = 0.85),
    hoverinfo = "x+y",
    hovertemplate = paste(
      "<b>%{x}</b><br>",
      "Total Sleep: %{y} minutes<br>",
      "<extra></extra>"
    )
  ) %>%
    layout(
      title = list(text = "Sleep Duration per Night", x = 0.5),
      xaxis = list(title = "", tickformat = "%b %d"),
      yaxis = list(title = "Minutes"),
      margin = list(l = 50, r = 20, t = 50, b = 40),
      hoverlabel = list(bgcolor = clr$bg)
    )
} else {
  create_empty_plot("No sleep data available")
}
```



### 30. Sleep Efficiency

Ratio of asleep minutes to total minutes in bed (including wake periods). How much time in bed was good sleep?

Note: What would this look like with a user with inefficient sleep?

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== SLEEP EFFICIENCY =====
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  sleep_efficiency <- sleep_data %>%
    group_by(dateOfSleep, logId) %>%
    summarise(
      asleep_minutes = sum(sleep_stage != "wake"),
      total_minutes = n(),
      .groups = "drop"
    ) %>%
    group_by(dateOfSleep) %>%
    summarise(
      asleep_minutes = sum(asleep_minutes),
      total_minutes = sum(total_minutes),
      efficiency = round(asleep_minutes / total_minutes * 100, 1),
      .groups = "drop"
    ) %>%
    mutate(dateOfSleep = as.Date(dateOfSleep))
  
  plot_ly() %>%
    add_trace(
      data = sleep_efficiency,
      x = ~dateOfSleep,
      y = ~efficiency,
      type = "scatter",
      mode = "lines+markers",
      line = list(color = clr$blue, width = 2),
      marker = list(color = clr$blue, size = 8),
      name = "Efficiency",
      hoverinfo = "x+y",
      hovertemplate = paste(
        "<b>%{x}</b><br>",
        "Efficiency: %{y}%<br>",
        "<extra></extra>"
      )
    ) %>%
    add_trace(
      x = ~range(sleep_efficiency$dateOfSleep),
      y = c(85, 85),
      type = "scatter",
      mode = "lines",
      line = list(color = clr$target_line, dash = "dash", width = 2),
      name = "Target (85%)",
      hoverinfo = "skip"
    ) %>%
    layout(
      title = list(text = "Sleep Efficiency", x = 0.5),
      xaxis = list(title = "", tickformat = "%b %d"),
      yaxis = list(title = "Efficiency (%)", range = c(60, 100)),
      margin = list(l = 50, r = 20, t = 50, b = 60),
      hoverlabel = list(bgcolor = clr$bg),
      legend = list(
        orientation = "h",
        yanchor = "top",
        y = -0.15,
        xanchor = "center",
        x = 0.5
      )
    )
} else {
  create_empty_plot("No sleep data available")
}

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$sleep_efficiency_chart <- renderPlotly({
#   req(sleep_data())
#
#   sleep_efficiency <- sleep_data() %>%
#     group_by(dateOfSleep, logId) %>%
#     summarise(
#       asleep_minutes = sum(sleep_stage != "wake"),
#       total_minutes = n(),
#       .groups = "drop"
#     ) %>%
#     group_by(dateOfSleep) %>%
#     summarise(
#       asleep_minutes = sum(asleep_minutes),
#       total_minutes = sum(total_minutes),
#       efficiency = round(asleep_minutes / total_minutes * 100, 1),
#       .groups = "drop"
#     ) %>%
#     mutate(dateOfSleep = as.Date(dateOfSleep))
#
#   if (nrow(sleep_efficiency) == 0) {
#     return(create_empty_plot("No sleep data available for selected filters"))
#   }
#
#   plot_ly() %>%
#     add_trace(
#       data = sleep_efficiency,
#       x = ~dateOfSleep,
#       y = ~efficiency,
#       type = "scatter",
#       mode = "lines+markers",
#       line = list(color = clr$blue, width = 2),
#       marker = list(color = clr$blue, size = 8),
#       name = "Efficiency",
#       hoverinfo = "x+y",
#       hovertemplate = paste(
#         "<b>%{x}</b><br>",
#         "Efficiency: %{y}%<br>",
#         "<extra></extra>"
#       )
#     ) %>%
#     add_trace(
#       x = ~range(sleep_efficiency$dateOfSleep),
#       y = c(85, 85),
#       type = "scatter",
#       mode = "lines",
#       line = list(color = clr$target_line, dash = "dash", width = 2),
#       name = "Target (85%)",
#       hoverinfo = "skip"
#     ) %>%
#     layout(
#       title = list(text = "Sleep Efficiency", x = 0.5),
#       xaxis = list(title = "", tickformat = "%b %d"),
#       yaxis = list(title = "Efficiency (%)", range = c(60, 100)),
#       margin = list(l = 50, r = 20, t = 50, b = 60),
#       hoverlabel = list(bgcolor = clr$bg),
#       legend = list(
#         orientation = "h",
#         yanchor = "top",
#         y = -0.15,
#         xanchor = "center",
#         x = 0.5
#       )
#     )
# })
```

### 31. Sleep Latency

Tells you how long it takes you to fall asleep.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== SLEEP LATENCY KPI (Fixed Date Order) =====
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  
  # Parse datetime
  sleep_clean <- sleep_data %>%
    mutate(
      datetime = ymd_hms(datetime),
      date = as.Date(dateOfSleep)
    ) %>%
    arrange(date, datetime)
  
  # Identify sleep sessions (gap > 2 hours)
  sleep_with_sessions <- sleep_clean %>%
    group_by(date) %>%
    arrange(datetime) %>%
    mutate(
      time_diff = ifelse(
        is.na(lag(datetime)), 
        0, 
        as.numeric(difftime(datetime, lag(datetime), units = "mins"))
      ),
      new_session = ifelse(
        is.na(lag(datetime)) | time_diff > 120,
        1,
        0
      ),
      session_id = cumsum(new_session)
    ) %>%
    ungroup()
  
  # Calculate sleep latency for each session
  latency_data <- sleep_with_sessions %>%
    group_by(date, session_id) %>%
    summarise(
      session_start = min(datetime),
      first_sleep_time = min(
        datetime[sleep_stage %in% c("asleep", "light", "deep", "rem")], 
        na.rm = TRUE
      ),
      sleep_latency_minutes = ifelse(
        !is.na(first_sleep_time),
        as.numeric(difftime(first_sleep_time, min(datetime), units = "mins")),
        NA
      ),
      .groups = "drop"
    ) %>%
    # KEY FIX: Sort by date and session_id BEFORE creating labels
    arrange(date, session_id) %>%
    mutate(
      # Create session label with proper ordering
      session_label = ifelse(
        duplicated(date),
        paste(format(date, "%b %d"), "(S", session_id, ")"),
        format(date, "%b %d")
      ),
      # Keep the factor levels in chronological order
      session_label = factor(session_label, levels = unique(session_label))
    )
  
  # Calculate average latency for KPI display
  avg_latency <- round(mean(latency_data$sleep_latency_minutes, na.rm = TRUE), 1)
  min_latency <- round(min(latency_data$sleep_latency_minutes, na.rm = TRUE), 1)
  max_latency <- round(max(latency_data$sleep_latency_minutes, na.rm = TRUE), 1)
  latest_latency <- round(tail(latency_data$sleep_latency_minutes, 1), 1)
  
  # Create the plot
  plot_ly(
    data = latency_data,
    x = ~session_label,
    y = ~sleep_latency_minutes,
    type = "scatter",
    mode = "lines+markers",
    line = list(color = "#2C3E50", width = 2),
    marker = list(
      color = ~sleep_latency_minutes,
      colorscale = list(c(0, "#27AE60"), c(0.5, "#F1C40F"), c(1, "#E74C3C")),
      size = 12,
      showscale = FALSE
    ),
    hovertemplate = paste(
      "<b>%{x}</b><br>",
      "Sleep Latency: %{y:.1f} minutes<br>",
      "<extra></extra>"
    )
  ) %>%
    layout(
      title = list(
        text = paste(
          "Sleep Latency",
          "<br>",
          "<sup>Average: ", avg_latency, " min | ",
          "Latest: ", latest_latency, " min | ",
          "Range: ", min_latency, " - ", max_latency, " min</sup>"
        ),
        x = 0.5
      ),
      xaxis = list(
        title = "",
        tickangle = -45,
        tickfont = list(size = 10),
        # Keep x-axis in the order of the factor levels
        type = "category"
      ),
      yaxis = list(
        title = "Minutes to Fall Asleep",
        range = c(0, max(latency_data$sleep_latency_minutes, na.rm = TRUE) * 1.2)
      ),
      margin = list(l = 50, r = 20, t = 80, b = 120),
      hoverlabel = list(bgcolor = "white"),
      # Add reference line for "good" latency (< 15 min)
      shapes = list(
        list(
          type = "line",
          x0 = 0,
          x1 = 1,
          xref = "paper",
          y0 = 15,
          y1 = 15,
          line = list(color = "#27AE60", dash = "dash", width = 1)
        ),
        list(
          type = "line",
          x0 = 0,
          x1 = 1,
          xref = "paper",
          y0 = 30,
          y1 = 30,
          line = list(color = "#F1C40F", dash = "dash", width = 1)
        )
      ),
      annotations = list(
        list(
          x = 1,
          y = 15,
          xref = "paper",
          yref = "y",
          text = "Good (< 15 min)",
          showarrow = FALSE,
          xanchor = "right",
          font = list(color = "#27AE60", size = 10)
        ),
        list(
          x = 1,
          y = 30,
          xref = "paper",
          yref = "y",
          text = "Fair (15-30 min)",
          showarrow = FALSE,
          xanchor = "right",
          font = list(color = "#F1C40F", size = 10)
        )
      )
    )
  
} else {
  create_empty_plot("No sleep data available")
}
```

### 32. Sleep Stage per Night

Daily breakdown showing minutes in EACH stage per night. How does my sleep composition change night-to-night?

Note: We should label the minutes.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== SLEEP STAGE STACKED BARS PER NIGHT =====
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  stacked_data <- sleep_data %>%
    filter(sleep_stage %in% c("deep", "rem", "light", "wake")) %>%
    group_by(dateOfSleep, sleep_stage) %>%
    summarise(minutes = n(), .groups = "drop") %>%
    mutate(
      sleep_stage = recode(sleep_stage,
                          deep = "Deep",
                          rem = "REM",
                          light = "Light",
                          wake = "Wake"),
      dateOfSleep = as.Date(dateOfSleep)
    )
  
  # Use ggplotly with explicit style() to preserve colors
  p <- ggplot(stacked_data, aes(x = dateOfSleep, y = minutes, fill = sleep_stage)) +
    geom_col(width = 0.7, alpha = 0.9) +
    scale_fill_manual(values = c(Deep = clr$deep, REM = clr$rem, Light = clr$light, Wake = clr$wake)) +
    scale_x_date(date_labels = "%b %d") +
    labs(x = NULL, y = "Minutes") +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
      panel.grid.major = element_line(color = clr$grid_line, linewidth = 0.3),
      panel.grid.minor = element_blank()
    )
  
  ggplotly(p, tooltip = c("x", "y", "fill")) %>%
    layout(
      title = list(text = "Sleep Stages per Night", x = 0.5),
      xaxis = list(title = ""),
      yaxis = list(title = "Minutes"),
      margin = list(l = 50, r = 20, t = 50, b = 40),
      hoverlabel = list(bgcolor = clr$bg),
      legend = list(
        orientation = "h",
        yanchor = "bottom",
        y = -0.15,
        xanchor = "center",
        x = 0.5
      )
    ) %>%
    style(
      marker = list(
        color = ~ifelse(sleep_stage == "Deep", clr$deep,
                 ifelse(sleep_stage == "REM", clr$rem,
                 ifelse(sleep_stage == "Light", clr$light,
                 clr$wake)))
      )
    )
} else {
  create_empty_plot("No sleep data available")
}

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$sleep_stages_chart <- renderPlotly({
#   req(sleep_data())
#
#   stacked_data <- sleep_data() %>%
#     filter(sleep_stage %in% c("deep", "rem", "light", "wake")) %>%
#     group_by(dateOfSleep, sleep_stage) %>%
#     summarise(minutes = n(), .groups = "drop") %>%
#     mutate(
#       sleep_stage = recode(sleep_stage,
#                           deep = "Deep",
#                           rem = "REM",
#                           light = "Light",
#                           wake = "Wake"),
#       dateOfSleep = as.Date(dateOfSleep)
#     )
#
#   if (nrow(stacked_data) == 0) {
#     return(create_empty_plot("No sleep data available for selected filters"))
#   }
#
#   # Use ggplotly with explicit style() to preserve colors
#   p <- ggplot(stacked_data, aes(x = dateOfSleep, y = minutes, fill = sleep_stage)) +
#     geom_col(width = 0.7, alpha = 0.9) +
#     scale_fill_manual(values = c(Deep = clr$deep, REM = clr$rem, Light = clr$light, Wake = clr$wake)) +
#     scale_x_date(date_labels = "%b %d") +
#     labs(x = NULL, y = "Minutes") +
#     theme_minimal() +
#     theme(
#       legend.position = "bottom",
#       plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
#       panel.grid.major = element_line(color = clr$grid_line, linewidth = 0.3),
#       panel.grid.minor = element_blank()
#     )
#
#   ggplotly(p, tooltip = c("x", "y", "fill")) %>%
#     layout(
#       title = list(text = "Sleep Stages per Night", x = 0.5),
#       xaxis = list(title = ""),
#       yaxis = list(title = "Minutes"),
#       margin = list(l = 50, r = 20, t = 50, b = 40),
#       hoverlabel = list(bgcolor = clr$bg),
#       legend = list(
#         orientation = "h",
#         yanchor = "bottom",
#         y = -0.15,
#         xanchor = "center",
#         x = 0.5
#       )
#     ) %>%
#     style(
#       marker = list(
#         color = ~ifelse(sleep_stage == "Deep", clr$deep,
#                  ifelse(sleep_stage == "REM", clr$rem,
#                  ifelse(sleep_stage == "Light", clr$light,
#                  clr$wake)))
#       )
#     )
# })
```

### Multiple Sleep Sessions per Day ❌

This stacked segmented bar chart visualizes the distribution of sleep stages (Deep, REM, Light, and Wake) across different sleep sessions, with each bar representing a distinct period of sleep on a given day. It answers questions like "How many distinct sleep sessions occurred each day?", "What's the composition of each sleep session in terms of sleep stages?", and "How does sleep quality differ between multiple sleep sessions on the same day?"

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== MULTIPLE SLEEP SESSIONS PER DAY =====
# if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
#   
#   # The 'datetime' column already contains the sleep minute timestamps
#   sleep_clean <- sleep_data %>%
#     mutate(
#       datetime = ymd_hms(datetime),  # Parse the sleep datetime
#       dateOfSleep = as.Date(dateOfSleep)
#     ) %>%
#     # Sort by date and time to identify gaps
#     arrange(dateOfSleep, datetime)
#   
#   # Identify sleep sessions based on time gaps (> 2 hours between records)
#   sleep_with_gaps <- sleep_clean %>%
#     group_by(dateOfSleep) %>%
#     arrange(datetime) %>%
#     mutate(
#       # Time difference from previous record in minutes
#       time_diff = ifelse(
#         is.na(lag(datetime)), 
#         0, 
#         as.numeric(difftime(datetime, lag(datetime), units = "mins"))
#       ),
#       # New session starts when gap > 120 minutes (2 hours)
#       new_session = ifelse(
#         is.na(lag(datetime)) | time_diff > 120,
#         1,
#         0
#       ),
#       # Create session ID within each day
#       session_id = cumsum(new_session)
#     ) %>%
#     ungroup()
#   
#   # Aggregate by session and sleep stage
#   session_data <- sleep_with_gaps %>%
#     filter(sleep_stage %in% c("deep", "rem", "light", "wake")) %>%
#     group_by(dateOfSleep, session_id, sleep_stage) %>%
#     summarise(
#       minutes = n(),
#       .groups = "drop"
#     ) %>%
#     mutate(
#       sleep_stage = recode(sleep_stage,
#                           deep = "Deep",
#                           rem = "REM", 
#                           light = "Light",
#                           wake = "Wake"),
#       # Create session label
#       session_label = paste(
#         format(dateOfSleep, "%b %d"),
#         "-",
#         paste0("Session ", session_id)
#       )
#     )
#   
#   # Check if we have data
#   if (nrow(session_data) > 0) {
#     
#     # Get distinct sessions in chronological order
#     sessions <- session_data %>%
#       group_by(dateOfSleep, session_id, session_label) %>%
#       summarise(.groups = "drop") %>%
#       arrange(dateOfSleep, session_id) %>%
#       pull(session_label)
#     
#     # Convert to factor to maintain order
#     session_data <- session_data %>%
#       mutate(session_label = factor(session_label, levels = sessions))
#     
#     # Create the plot
#     plot_ly(
#       data = session_data,
#       x = ~session_label,
#       y = ~minutes,
#       color = ~sleep_stage,
#       colors = c(Deep = clr$deep, REM = clr$rem, Light = clr$light, Wake = clr$wake),
#       type = "bar",
#       hovertemplate = paste(
#         "<b>%{x}</b><br>",
#         "%{data.name}: %{y} minutes<br>",
#         "<extra></extra>"
#       )
#     ) %>%
#       layout(
#         barmode = "stack",
#         title = list(text = "Sleep Sessions per Day", x = 0.5),
#         xaxis = list(
#           title = "",
#           tickangle = -45,
#           tickfont = list(size = 10)
#         ),
#         yaxis = list(title = "Minutes"),
#         margin = list(l = 50, r = 20, t = 50, b = 100),
#         hoverlabel = list(bgcolor = clr$bg),
#         legend = list(
#           orientation = "h",
#           yanchor = "bottom",
#           y = -0.15,
#           xanchor = "center",
#           x = 0.5,
#           bgcolor = "rgba(255,255,255,0.8)"
#         )
#       )
#   } else {
#     create_empty_plot("No sleep stage data available for sessions")
#   }
#   
# } else {
#   create_empty_plot("No sleep data available")
# }
```

### Breathing Rate ❌

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== COMBINE SLEEP START (from minute data) WITH BREATHING RATE DATA =====
# 
# # 1. Get sleep session start times from minute-level data
# sleep_starts <- sleep_data %>%
#   mutate(
#     datetime = ymd_hms(datetime),
#     date = as.Date(dateOfSleep)
#   ) %>%
#   arrange(date, datetime) %>%
#   group_by(date) %>%
#   mutate(
#     time_diff = ifelse(
#       is.na(lag(datetime)), 
#       0, 
#       as.numeric(difftime(datetime, lag(datetime), units = "mins"))
#     ),
#     new_session = ifelse(
#       is.na(lag(datetime)) | time_diff > 120,
#       1,
#       0
#     ),
#     session_id = cumsum(new_session)
#   ) %>%
#   ungroup() %>%
#   # Get unique sessions with their start times
#   group_by(date, session_id) %>%
#   summarise(
#     sleep_start = min(datetime),
#     .groups = "drop"
#   ) %>%
#   # Now create labels outside the grouped summarise
#   group_by(date) %>%
#   mutate(
#     total_sessions = n(),
#     session_label = ifelse(
#       total_sessions > 1,
#       paste(format(date, "%b %d"), "Session", session_id),
#       format(date, "%b %d")
#     )
#   ) %>%
#   ungroup() %>%
#   arrange(date, session_id)
# 
# # 2. Merge with breathing rate data using the date field
# breathing_with_starts <- breathing_rate_summary %>%
#   mutate(
#     date = as.Date(date),
#     sleep_end = ymd_hms(sleep_end)
#   ) %>%
#   # Join on date to get sleep start times
#   left_join(
#     sleep_starts %>% select(date, session_id, sleep_start, session_label),
#     by = "date"
#   ) %>%
#   # Handle cases where there are multiple sleep sessions per day
#   group_by(date) %>%
#   mutate(
#     # Calculate which sleep session this breathing data belongs to
#     # Based on the sleep_end time relative to sleep_start
#     session_match = ifelse(
#       n() == 1,
#       session_id,
#       case_when(
#         # If multiple sessions, match by proximity of sleep_end to sleep_start
#         session_id == which.min(abs(hour(sleep_end) - hour(sleep_start))) ~ session_id,
#         TRUE ~ NA_real_
#       )
#     )
#   ) %>%
#   ungroup() %>%
#   # Keep only matched rows
#   filter(!is.na(session_match)) %>%
#   # Clean up the label
#   mutate(
#     label = ifelse(
#       duplicated(date),
#       paste(format(date, "%b %d"), "Session", session_match),
#       format(date, "%b %d")
#     ),
#     # Create a time label showing both start and end
#     time_range = paste(
#       format(sleep_start, "%I:%M %p"),
#       "-",
#       format(sleep_end, "%I:%M %p")
#     )
#   )
# 
# # 3. Create the improved breathing rate chart
# if (exists("breathing_with_starts") && nrow(breathing_with_starts) > 0) {
#   
#   # Sort by date and session
#   breathing_plot_data <- breathing_with_starts %>%
#     arrange(date, session_match) %>%
#     mutate(
#       label = factor(label, levels = unique(label))
#     )
#   
#   plot_ly() %>%
#     # Full sleep breathing rate
#     add_trace(
#       data = breathing_plot_data,
#       x = ~label,
#       y = ~full_sleep_breathing_rate,
#       name = "Full Sleep",
#       type = "scatter",
#       mode = "lines+markers",
#       line = list(color = "#2C3E50", width = 3),
#       marker = list(color = "#2C3E50", size = 8),
#       hovertemplate = paste(
#         "<b>%{x}</b><br>",
#         "Time: %{customdata}<br>",
#         "Full Sleep: %{y:.1f} breaths/min<br>",
#         "<extra></extra>"
#       ),
#       customdata = ~time_range
#     ) %>%
#     # Deep sleep breathing rate
#     add_trace(
#       data = breathing_plot_data,
#       x = ~label,
#       y = ~deep_sleep_breathing_rate,
#       name = "Deep Sleep",
#       type = "scatter",
#       mode = "lines+markers",
#       line = list(color = clr$deep, width = 2, dash = "dash"),
#       marker = list(color = clr$deep, size = 6),
#       hovertemplate = paste(
#         "<b>%{x}</b><br>",
#         "Deep Sleep: %{y:.1f} breaths/min<br>",
#         "<extra></extra>"
#       )
#     ) %>%
#     # Light sleep breathing rate
#     add_trace(
#       data = breathing_plot_data,
#       x = ~label,
#       y = ~light_sleep_breathing_rate,
#       name = "Light Sleep",
#       type = "scatter",
#       mode = "lines+markers",
#       line = list(color = clr$light, width = 2, dash = "dash"),
#       marker = list(color = clr$light, size = 6),
#       hovertemplate = paste(
#         "<b>%{x}</b><br>",
#         "Light Sleep: %{y:.1f} breaths/min<br>",
#         "<extra></extra>"
#       )
#     ) %>%
#     # REM sleep breathing rate
#     add_trace(
#       data = breathing_plot_data,
#       x = ~label,
#       y = ~rem_sleep_breathing_rate,
#       name = "REM Sleep",
#       type = "scatter",
#       mode = "lines+markers",
#       line = list(color = clr$rem, width = 2, dash = "dash"),
#       marker = list(color = clr$rem, size = 6),
#       hovertemplate = paste(
#         "<b>%{x}</b><br>",
#         "REM Sleep: %{y:.1f} breaths/min<br>",
#         "<extra></extra>"
#       )
#     ) %>%
#     layout(
#       title = list(
#         text = paste(
#           "Breathing Rate by Sleep Session",
#           "<br>",
#           "<sup>Hover for start & end times</sup>"
#         ),
#         x = 0.5
#       ),
#       xaxis = list(
#         title = "",
#         tickangle = -45,
#         tickfont = list(size = 10),
#         type = "category"
#       ),
#       yaxis = list(
#         title = "Breaths per Minute",
#         range = c(12, 19)
#       ),
#       margin = list(l = 50, r = 20, t = 80, b = 120),
#       hoverlabel = list(bgcolor = clr$bg),
#       legend = list(
#         orientation = "h",
#         yanchor = "bottom",
#         y = -0.25,
#         xanchor = "center",
#         x = 0.5,
#         bgcolor = "rgba(255,255,255,0.8)"
#       )
#     )
#   
# } else {
#   create_empty_plot("No matched sleep-breathing data available")
# }
```

## Professors Charts

### HRV Over the Week

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== CHART 1: HRV LINE PLOT OVER WEEK =====
# Calculate daily average HRV for cleaner visualization
hrv_daily <- hrv_data %>%
  mutate(date_only = as.Date(datetime)) %>%
  group_by(date_only) %>%
  summarise(
    avg_rmssd = mean(rmssd_ms, na.rm = TRUE),
    sd_rmssd = sd(rmssd_ms, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>%
  filter(!is.na(avg_rmssd))

if (exists("hrv_daily") && nrow(hrv_daily) > 0) {
  plot_ly() %>%
    # Add ribbon for standard deviation (optional)
    add_ribbons(
      data = hrv_daily,
      x = ~date_only,
      ymin = ~avg_rmssd - sd_rmssd,
      ymax = ~avg_rmssd + sd_rmssd,
      name = "±1 SD",
      color = I(clr$hr),
      opacity = 0.2,
      showlegend = FALSE
    ) %>%
    # Add daily average points with line
    add_trace(
      data = hrv_daily,
      x = ~date_only,
      y = ~avg_rmssd,
      type = "scatter",
      mode = "lines+markers",
      name = "Avg Daily HRV",
      line = list(color = clr$hr, width = 2),
      marker = list(color = clr$hr, size = 8),
      hovertemplate = paste(
        "<b>%{x}</b><br>",
        "Avg HRV: %{y:.1f} ms<br>",
        "SD: %{customdata:.1f} ms<br>",
        "Readings: %{text}<extra></extra>"
      ),
      customdata = ~sd_rmssd,
      text = ~n
    ) %>%
    # Add a reference line for typical baseline
    add_trace(
      x = range(hrv_daily$date_only),
      y = c(20, 20),
      type = "scatter",
      mode = "lines",
      line = list(color = clr$target_line, dash = "dash", width = 1),
      name = "Baseline (20 ms)",
      hoverinfo = "skip"
    ) %>%
    layout(
      title = list(text = "Heart Rate Variability (HRV) Over the Week", x = 0.5),
      xaxis = list(title = "", tickformat = "%b %d", dtick = 86400000),
      yaxis = list(title = "RMSSD (ms)", range = c(0, max(hrv_daily$avg_rmssd + 10, 25))),
      hoverlabel = list(bgcolor = clr$bg),
      margin = list(l = 50, r = 20, t = 50, b = 40),
      legend = list(
        orientation = "h",
        yanchor = "top",
        y = -0.15,
        xanchor = "center",
        x = 0.5
      )
    )
} else {
  create_empty_plot("No HRV data available")
}
```

### HRV Heatmap (Days x Hours)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== CHART 2: HRV HEATMAP =====
# Prepare data: group by date and hour
hrv_heatmap_data <- hrv_data %>%
  mutate(
    date_only = as.Date(datetime),
    hour_only = hour(datetime)
  ) %>%
  group_by(date_only, hour_only) %>%
  summarise(
    avg_rmssd = mean(rmssd_ms, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # Complete missing hours with NA (so they show as blank)
  complete(date_only, hour_only = 0:23) %>%
  # Filter to the date range of interest
  filter(date_only >= as.Date("2026-05-28"), date_only <= as.Date("2026-06-08"))

if (exists("hrv_heatmap_data") && nrow(hrv_heatmap_data) > 0) {
  # Create the heatmap
  plot_ly(
    data = hrv_heatmap_data,
    x = ~hour_only,
    y = ~date_only,
    z = ~avg_rmssd,
    type = "heatmap",
    colorscale = list(
      c(0, "#2C3E50"),   # Low HRV (dark)
      c(0.5, clr$hr),    # Medium HRV
      c(1, "#2ECC71")    # High HRV (green)
    ),
    zmin = 5,
    zmax = 40,
    hovertemplate = paste(
      "<b>%{y}</b><br>",
      "Hour: %{x}:00<br>",
      "Avg HRV: %{z:.1f} ms<extra></extra>"
    ),
    colorbar = list(
      title = list(text = "RMSSD (ms)", side = "right"),
      len = 0.8
    )
  ) %>%
    layout(
      title = list(text = "HRV Heatmap - Hour of Day vs Date", x = 0.5),
      xaxis = list(
        title = "Hour of Day",
        tickmode = "array",
        tickvals = seq(0, 23, by = 2),
        ticktext = sprintf("%02d:00", seq(0, 23, by = 2))
      ),
      yaxis = list(
        title = "Date",
        tickformat = "%b %d",
        autorange = "reversed"  # Most recent date at top
      ),
      margin = list(l = 50, r = 50, t = 50, b = 40),
      hoverlabel = list(bgcolor = clr$bg)
    )
} else {
  create_empty_plot("No HRV heatmap data available")
}
```

### Heart Rate Heatmap

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== CHART 3: HEART RATE HEATMAP =====
# Prepare data: group by date and hour
hr_heatmap_data <- hr_data %>%
  mutate(
    date_only = as.Date(datetime),
    hour_only = hour(datetime)
  ) %>%
  group_by(date_only, hour_only) %>%
  summarise(
    avg_hr = mean(heart_rate_avg, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  complete(date_only, hour_only = 0:23) %>%
  filter(date_only >= as.Date("2026-05-28"), date_only <= as.Date("2026-06-08"))

if (exists("hr_heatmap_data") && nrow(hr_heatmap_data) > 0) {
  plot_ly(
    data = hr_heatmap_data,
    x = ~hour_only,
    y = ~date_only,
    z = ~avg_hr,
    type = "heatmap",
    colorscale = list(
      c(0, "#2C3E50"),     # Low HR (dark)
      c(0.3, clr$hr),      # Medium HR
      c(0.7, "#E67E22"),   # High HR
      c(1, "#E74C3C")      # Very high HR (red)
    ),
    zmin = 55,
    zmax = 120,
    hovertemplate = paste(
      "<b>%{y}</b><br>",
      "Hour: %{x}:00<br>",
      "Avg HR: %{z:.0f} bpm<extra></extra>"
    ),
    colorbar = list(
      title = list(text = "Avg HR (bpm)", side = "right"),
      len = 0.8
    )
  ) %>%
    layout(
      title = list(text = "Heart Rate Heatmap - Hour of Day vs Date", x = 0.5),
      xaxis = list(
        title = "Hour of Day",
        tickmode = "array",
        tickvals = seq(0, 23, by = 2),
        ticktext = sprintf("%02d:00", seq(0, 23, by = 2))
      ),
      yaxis = list(
        title = "Date",
        tickformat = "%b %d",
        autorange = "reversed"
      ),
      margin = list(l = 50, r = 50, t = 50, b = 40),
      hoverlabel = list(bgcolor = clr$bg)
    )
} else {
  create_empty_plot("No heart rate heatmap data available")
}
```

### Breathing Rate Line Plot

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== CHART 4: BREATHING RATE LINE PLOT =====
if (exists("breathing_data") && !is.null(breathing_data) && nrow(breathing_data) > 0) {
  
  # Reshape data for easier plotting
  breathing_long <- breathing_data %>%
    pivot_longer(
      cols = c(full_sleep_breathing_rate, deep_sleep_breathing_rate, 
               light_sleep_breathing_rate, rem_sleep_breathing_rate),
      names_to = "sleep_stage",
      values_to = "breathing_rate"
    ) %>%
    mutate(
      sleep_stage = recode(sleep_stage,
                          full_sleep_breathing_rate = "Full Sleep",
                          deep_sleep_breathing_rate = "Deep",
                          light_sleep_breathing_rate = "Light",
                          rem_sleep_breathing_rate = "REM"),
      date = as.Date(date)
    ) %>%
    filter(!is.na(breathing_rate))
  
  # Colors for each stage
  stage_colors <- c(
    "Full Sleep" = clr$text_primary,
    "Deep" = clr$deep,
    "Light" = clr$light,
    "REM" = clr$rem
  )
  
  # Line widths - full sleep is thicker
  stage_linewidth <- c(
    "Full Sleep" = 2.5,
    "Deep" = 1.5,
    "Light" = 1.5,
    "REM" = 1.5
  )
  
  # Create the plot
  p <- ggplot(breathing_long, aes(x = date, y = breathing_rate, color = sleep_stage, group = sleep_stage)) +
    geom_line(aes(linewidth = sleep_stage), alpha = 0.9) +
    scale_color_manual(values = stage_colors) +
    scale_linewidth_manual(values = stage_linewidth) +
    labs(
      x = NULL,
      y = "Breaths per Minute"
    ) +
    scale_x_date(date_labels = "%b %d") +
    scale_y_continuous(limits = c(12, 19), breaks = seq(12, 19, by = 1)) +
    dash_theme() +
    theme(
      legend.position = "bottom",
      legend.title = element_blank()
    )
  
  # Convert to interactive
  ggplotly(p, tooltip = c("x", "y", "color")) %>%
    layout(
      title = list(text = "Breathing Rate by Sleep Stage", x = 0.5),
      hoverlabel = list(bgcolor = clr$bg),
      margin = list(l = 50, r = 20, t = 50, b = 40),
      legend = list(
        orientation = "h",
        yanchor = "bottom",
        y = -0.2,
        xanchor = "center",
        x = 0.5
      )
    )
  
} else {
  create_empty_plot("No breathing rate data available")
}
```

### SpO2 Line Plot

```{r, echo=FALSE, warning=FALSE, message=FALSE}

if (exists("spo2_data") && !is.null(spo2_data) && nrow(spo2_data) > 0) {
  
  spo2_daily <- spo2_data %>%
    mutate(date_only = as.Date(datetime)) %>%
    group_by(date_only) %>%
    summarise(
      avg_spo2 = mean(value, na.rm = TRUE),
      min_spo2 = min(value, na.rm = TRUE),
      max_spo2 = max(value, na.rm = TRUE),
      sd_spo2 = sd(value, na.rm = TRUE),
      n = n(),
      .groups = "drop"
    ) %>%
    filter(n >= 5)
  
  if (nrow(spo2_daily) > 0) {
    
    plot_ly() %>%
      # Min-Max range as filled area
      add_trace(
        data = spo2_daily,
        x = ~date_only,
        y = ~max_spo2,
        type = "scatter",
        mode = "lines",
        fill = "tonexty",
        fillcolor = paste0(clr$light_blue, "33"),
        line = list(color = "transparent"),
        name = "Range",
        showlegend = TRUE
      ) %>%
      add_trace(
        data = spo2_daily,
        x = ~date_only,
        y = ~min_spo2,
        type = "scatter",
        mode = "lines",
        fill = "tonexty",
        fillcolor = paste0(clr$light_blue, "33"),
        line = list(color = "transparent"),
        name = "Range",
        showlegend = FALSE
      ) %>%
      # Average line
      add_trace(
        data = spo2_daily,
        x = ~date_only,
        y = ~avg_spo2,
        type = "scatter",
        mode = "lines+markers",
        name = "Avg SpO2",
        line = list(color = clr$blue, width = 2),
        marker = list(color = clr$blue, size = 6),
        error_y = list(
          type = "data",
          array = ~sd_spo2,
          color = clr$error_bar
        ),
        hovertemplate = paste(
          "<b>%{x}</b><br>",
          "Avg: %{y:.1f}%<br>",
          "Min: %{customdata[0]:.1f}%<br>",
          "Max: %{customdata[1]:.1f}%<br>",
          "Readings: %{customdata[2]}<extra></extra>"
        ),
        customdata = ~cbind(min_spo2, max_spo2, n)
      ) %>%
      # Reference line
      add_trace(
        x = range(spo2_daily$date_only),
        y = c(95, 95),
        type = "scatter",
        mode = "lines",
        line = list(color = clr$target_line, dash = "dash", width = 1),
        name = "Normal (95%)",
        hoverinfo = "skip"
      ) %>%
      layout(
        title = list(text = "Blood Oxygen Saturation (SpO2) Over Time", x = 0.5),
        xaxis = list(title = "", tickformat = "%b %d"),
        yaxis = list(title = "SpO2 (%)", range = c(88, 100)),
        hoverlabel = list(bgcolor = clr$bg),
        margin = list(l = 50, r = 20, t = 50, b = 40),
        legend = list(
          orientation = "h",
          yanchor = "top",
          y = -0.15,
          xanchor = "center",
          x = 0.5
        )
      )
    
  } else {
    create_empty_plot("No daily SpO2 data available (needs at least 5 readings per day)")
  }
} else {
  create_empty_plot("No SpO2 data available")
}
```

### HRV vs Sleep

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== CHART 6: HRV vs SLEEP MINUTES (WITH LAG) =====

# 1. Calculate daily sleep total minutes
if (exists("sleep_data") && exists("hrv_data") && 
    !is.null(sleep_data) && nrow(sleep_data) > 0 && 
    !is.null(hrv_data) && nrow(hrv_data) > 0) {
  
  # Daily sleep minutes
  sleep_daily <- sleep_data %>%
    group_by(dateOfSleep) %>%
    summarise(
      total_sleep_minutes = n(),
      .groups = "drop"
    ) %>%
    rename(date = dateOfSleep)
  
  # Daily HRV average
  hrv_daily_full <- hrv_data %>%
    mutate(date = as.Date(datetime)) %>%
    group_by(date) %>%
    summarise(
      hrv_avg = mean(rmssd_ms, na.rm = TRUE),
      .groups = "drop"
    )
  
  # Merge sleep and HRV data
  hrv_sleep_data <- sleep_daily %>%
    full_join(hrv_daily_full, by = "date") %>%
    filter(!is.na(total_sleep_minutes), !is.na(hrv_avg)) %>%
    arrange(date)
  
  if (nrow(hrv_sleep_data) > 0) {
    
    # Create lagged variables
    hrv_sleep_lag <- hrv_sleep_data %>%
      mutate(
        # Sleep minutes (current and lagged)
        sleep_minutes = total_sleep_minutes,
        sleep_minutes_lag1 = lag(total_sleep_minutes, 1),
        sleep_minutes_lag2 = lag(total_sleep_minutes, 2),
        
        # HRV (current and lagged)
        hrv_current = hrv_avg,
        hrv_lag1 = lag(hrv_avg, 1),
        hrv_lag2 = lag(hrv_avg, 2)
      ) %>%
      filter(!is.na(hrv_current), !is.na(sleep_minutes))
    
    # Create plot with multiple traces
    plot_ly() %>%
      # Current day: Sleep vs HRV (same day)
      add_trace(
        data = hrv_sleep_lag,
        x = ~sleep_minutes,
        y = ~hrv_current,
        type = "scatter",
        mode = "markers",
        name = "Same Day",
        marker = list(
          color = clr$hr,
          size = 10,
          opacity = 0.8
        ),
        text = ~paste(
          "Date:", format(date, "%b %d"),
          "<br>Sleep:", sleep_minutes, "min",
          "<br>HRV:", round(hrv_current, 1), "ms"
        ),
        hoverinfo = "text"
      ) %>%
      # Previous day sleep vs current HRV (sleep -> HRV)
      add_trace(
        data = hrv_sleep_lag %>% filter(!is.na(sleep_minutes_lag1)),
        x = ~sleep_minutes_lag1,
        y = ~hrv_current,
        type = "scatter",
        mode = "markers",
        name = "Sleep → HRV (1-day lag)",
        marker = list(
          color = clr$blue,
          size = 10,
          opacity = 0.8,
          symbol = "square"
        ),
        text = ~paste(
          "Sleep Date:", format(date - 1, "%b %d"),
          "<br>Sleep:", sleep_minutes_lag1, "min",
          "<br>Next Day HRV:", round(hrv_current, 1), "ms"
        ),
        hoverinfo = "text"
      ) %>%
      # Current HRV vs next day sleep (HRV -> sleep)
      add_trace(
        data = hrv_sleep_lag %>% filter(!is.na(hrv_lag1)),
        x = ~sleep_minutes,
        y = ~hrv_lag1,
        type = "scatter",
        mode = "markers",
        name = "HRV → Sleep (1-day lag)",
        marker = list(
          color = clr$green,
          size = 10,
          opacity = 0.8,
          symbol = "diamond"
        ),
        text = ~paste(
          "HRV Date:", format(date, "%b %d"),
          "<br>HRV:", round(hrv_lag1, 1), "ms",
          "<br>Next Day Sleep:", sleep_minutes, "min"
        ),
        hoverinfo = "text"
      ) %>%
      # Add trend lines (optional - only if we have enough data)
      layout(
        title = list(
          text = "HRV vs Sleep Minutes (with Lag Analysis)",
          x = 0.5
        ),
        xaxis = list(
          title = "Sleep Minutes",
          range = c(0, max(hrv_sleep_lag$sleep_minutes, 
                          hrv_sleep_lag$sleep_minutes_lag1, na.rm = TRUE) + 50)
        ),
        yaxis = list(
          title = "HRV (RMSSD ms)",
          range = c(0, max(hrv_sleep_lag$hrv_current, 
                          hrv_sleep_lag$hrv_lag1, na.rm = TRUE) + 10)
        ),
        margin = list(l = 50, r = 20, t = 60, b = 40),
        hoverlabel = list(bgcolor = clr$bg),
        legend = list(
          orientation = "h",
          yanchor = "top",
          y = -0.2,
          xanchor = "center",
          x = 0.5
        ),
        annotations = list(
          list(
            x = 0.5,
            y = 1.02,
            xref = "paper",
            yref = "paper",
            text = "• Same Day: HRV vs sleep on same date<br>• Sleep → HRV: Does sleep affect next day's HRV?<br>• HRV → Sleep: Does HRV affect next day's sleep?",
            showarrow = FALSE,
            font = list(size = 10, color = clr$text_secondary),
            align = "center"
          )
        )
      )
    
  } else {
    create_empty_plot("No overlapping sleep and HRV data")
  }
  
} else {
  create_empty_plot("Sleep or HRV data not available")
}
```

### HRV vs Sleep Min

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== CHART 7: HRV vs SLEEP MINUTES - SCATTER WITH REGRESSION =====
# This is a simpler version focusing on the same-day relationship

if (exists("hrv_sleep_data") && nrow(hrv_sleep_data) > 0) {
  
  # Calculate correlation
  cor_value <- cor(hrv_sleep_data$total_sleep_minutes, 
                   hrv_sleep_data$hrv_avg, 
                   use = "complete.obs")
  
  # Create ggplot with regression line
  p <- ggplot(hrv_sleep_data, aes(x = total_sleep_minutes, y = hrv_avg)) +
    geom_point(color = clr$hr, size = 3, alpha = 0.7) +
    geom_smooth(method = "lm", se = TRUE, color = clr$blue, 
                fill = clr$hr, alpha = 0.2) +
    labs(
      x = "Total Sleep Minutes",
      y = "Average HRV (RMSSD ms)"
    ) +
    annotate("text", 
             x = max(hrv_sleep_data$total_sleep_minutes) * 0.75,
             y = max(hrv_sleep_data$hrv_avg) * 0.95,
             label = paste("r =", round(cor_value, 2)),
             size = 4,
             color = clr$text_secondary) +
    dash_theme()
  
  ggplotly(p, tooltip = c("x", "y")) %>%
    layout(
      title = list(text = "HRV vs Sleep Minutes", x = 0.5),
      hoverlabel = list(bgcolor = clr$bg),
      margin = list(l = 50, r = 20, t = 50, b = 40)
    )
  
} else {
  create_empty_plot("No data available for HRV vs Sleep correlation")
}
```

###

```{r, echo=FALSE, warning=FALSE, message=FALSE}

```

###

```{r, echo=FALSE, warning=FALSE, message=FALSE}

```

###

```{r, echo=FALSE, warning=FALSE, message=FALSE}

```

###

```{r, echo=FALSE, warning=FALSE, message=FALSE}

```

###

```{r, echo=FALSE, warning=FALSE, message=FALSE}

```

###

```{r, echo=FALSE, warning=FALSE, message=FALSE}

```