---
title: "Example Charts for Fitbit Dashboard"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# SET UP WORKBOOK 
library(tidyverse)
library(lubridate)
library(plotly)
library(scales)
library(zoo)
library(knitr)
library(see)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Load all CSV files from csvdata ------------------------------------

# Get list of all CSV files in csvdata folder
csv_files <- list.files("csvdata", pattern = "\\.csv$", full.names = FALSE)

# Remove .csv extension to use as variable names
file_names <- gsub("\\.csv$", "", csv_files)

# Load each file into a variable with the same name
for (i in seq_along(csv_files)) {
  file_path <- file.path("csvdata", csv_files[i])
  var_name <- file_names[i]
  assign(var_name, read.csv(file_path, stringsAsFactors = FALSE))
  cat("Loaded:", var_name, "-", nrow(get(var_name)), "rows\n")
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Helper functions -----------------------------------------

# SANITIZE COLUMN NAMES: Handle old CSV files and standardize naming
# This ensures compatibility whether data was generated by new or old Excel scripts
sanitize_column_names <- function(df) {
  names(df) <- gsub("-", "_", names(df))
  names(df) <- sub("^participantId$", "participantID", names(df))
  return(df)
}

# Apply column name sanitization to all loaded data frames
# This fixes: hyphens → underscores, and "participantId" → "participantID"
all_data_frames <- ls()[sapply(ls(), function(x) is.data.frame(get(x)))]
for (df_name in all_data_frames) {
  df <- get(df_name)
  df_cleaned <- sanitize_column_names(df)
  assign(df_name, df_cleaned)
  # Report what changed (optional)
  if (!identical(names(df), names(df_cleaned))) {
    cat("✓ Sanitized column names in:", df_name, "\n")
  }
}

# Helper: Convert date+time columns to datetime (handles 1899 Excel bug)
add_datetime_column <- function(df) {
  if (!is.null(df) && nrow(df) > 0 && "date" %in% names(df) && "time" %in% names(df)) {
    df %>%
      mutate(
        # Extract HH:MM:SS if present; if bare date only (midnight), use "00:00:00"
        time_clean = case_when(
          str_detect(time, "\\d{2}:\\d{2}:\\d{2}") ~ str_extract(time, "\\d{2}:\\d{2}:\\d{2}"),
          TRUE ~ "00:00:00"   # bare "1899-12-31" = midnight
        ),
        datetime = as.POSIXct(paste(date, time_clean), 
                              format = "%Y-%m-%d %H:%M:%S", tz = "UTC")
      ) %>%
      select(-time_clean)
  } else {
    df
  }
}

# Helper: Convert ISO timestamp to datetime (used by HRV, sessions, etc.)
add_datetime_from_timestamp <- function(df, timestamp_col = "timestamp") {
  if (!is.null(df) && nrow(df) > 0 && timestamp_col %in% names(df)) {
    df$datetime <- as.POSIXct(df[[timestamp_col]], format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
  }
  return(df)
}

#' Zero-fill a sparse intraday dataframe to a complete 5-minute grid
#' Adds rows with value = 0 for any missing 5-min slot within each date
zero_fill_5min <- function(df, value_col) {
  df %>%
    mutate(date_only = as.Date(datetime)) %>%
    group_by(participantID, date_only) %>%
    complete(
      datetime = seq(
        from = as.POSIXct(paste(unique(date_only), "00:00:00"), tz = "UTC"),
        to   = as.POSIXct(paste(unique(date_only), "23:55:00"), tz = "UTC"),
        by   = "5 min"
      )
    ) %>%
    mutate(across(all_of(value_col), ~ replace_na(., 0))) %>%
    ungroup() %>%
    select(-date_only)
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Source colour palette
source("R/colours.R")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Theme ------------------------
dash_theme <- function() {
  theme_minimal() +
    theme(
      # Grid lines - subtle
      panel.grid.major = element_line(color = clr$grid_line, linewidth = 0.3),
      panel.grid.minor = element_blank(),
      
      # Axis text
      axis.text = element_text(size = 10, color = clr$text_secondary),
      axis.title = element_text(size = 11, color = clr$text_secondary, face = "bold"),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)),
      
      # Legend
      legend.position = "bottom",
      legend.text = element_text(size = 10, color = clr$text_secondary),
      legend.title = element_blank(),
      
      # Title
      plot.title = element_text(size = 14, face = "bold", color = clr$text_primary, margin = margin(b = 10)),
      
      # Background - transparent for CSS compatibility
      plot.background = element_rect(fill = "transparent", color = NA),
      panel.background = element_rect(fill = "transparent", color = NA),
      legend.background = element_rect(fill = "transparent", color = NA)
    )
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# PREPARE DATA - Following app.R patterns -------------------------------------------

# Prepare HR data (date+time columns)
hr_data <- hr_intraday_5m %>%
  add_datetime_column() %>%
  filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220)

# Prepare Steps data (date+time columns)
steps_data <- steps_intraday_5m %>%
  add_datetime_column() %>%
  filter(!is.na(datetime))

# Prepare Distance data (date+time columns)
if (exists("distance_intraday")) {
  distance_data <- distance_intraday %>%
    add_datetime_column() %>%
    filter(!is.na(datetime))
}

# Prepare Activity Level data (date+time columns)
activity_level_data <- activity_level_intraday %>%
  add_datetime_column() %>%
  filter(!is.na(datetime))

# Prepare Zone Minutes data (date+time columns)
zone_data <- zone_minutes_intraday_5m %>%
  add_datetime_column() %>%
  filter(!is.na(datetime))

# Prepare HRV data (timestamp column - different format!)
hrv_data <- hrv_intraday %>%
  add_datetime_from_timestamp() %>%
  filter(!is.na(datetime), rmssd_ms > 0, rmssd_ms < 200)

# Add rolling average for HRV (as in app.R)
hrv_data <- hrv_data %>%
  arrange(datetime) %>%
  mutate(
    rolling_avg = zoo::rollapply(rmssd_ms, width = min(10, n()), 
                                 FUN = mean, fill = NA, align = "center")
  )

# Prepare Sleep data (ensure date column is proper Date type)
sleep_data <- sleep_minute %>%
  mutate(dateOfSleep = as.Date(dateOfSleep))

# Prepare Activity Sessions (needs start/end datetimes)
if (exists("activity_sessions")) {
  activity_sessions_data <- activity_sessions %>%
    mutate(
      start_datetime = as.POSIXct(start_time, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
      end_datetime = as.POSIXct(end_time, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
    ) %>%
    filter(!is.na(start_datetime))
}

# Prepare Sedentary Periods (needs start/end datetimes)
if (exists("sedentary_periods")) {
  sedentary_data <- sedentary_periods %>%
    mutate(
      start_datetime = as.POSIXct(period_start, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
      end_datetime = as.POSIXct(period_end, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
    ) %>%
    filter(!is.na(start_datetime))
}

# Prepare SpO2 data (with validation bounds)
if (exists("spo2_intraday")) {
  spo2_data <- spo2_intraday %>%
    add_datetime_from_timestamp() %>%
    filter(!is.na(datetime), value > 70, value < 100)  # Remove invalid readings
}

# Prepare Breathing Rate data
if (exists("breathing_rate_summary")) {
  breathing_data <- breathing_rate_summary %>%
    mutate(date = as.Date(date))
}
```

## Overview Tab

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== KPI: Average Heart Rate =====
if (exists("hr_data") && !is.null(hr_data) && nrow(hr_data) > 0) {
  avg_hr <- mean(hr_data$heart_rate_avg, na.rm = TRUE)
  kpi_hr <- round(avg_hr)
} else {
  kpi_hr <- NA
}

# ===== KPI: Average Daily Steps =====
if (exists("steps_data") && !is.null(steps_data) && nrow(steps_data) > 0) {
  daily_steps <- steps_data %>%
    mutate(date = as.Date(date)) %>%
    group_by(date) %>%
    summarise(total = sum(steps_5min, na.rm = TRUE))
  kpi_steps <- round(mean(daily_steps$total, na.rm = TRUE))
} else {
  kpi_steps <- NA
}

# ===== KPI: Average Deep Sleep =====
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  deep_by_night <- sleep_data %>%
    filter(sleep_stage == "deep") %>%
    group_by(dateOfSleep) %>%
    summarise(deep_minutes = n())
  kpi_sleep <- round(mean(deep_by_night$deep_minutes, na.rm = TRUE), 0)
} else {
  kpi_sleep <- NA
}

# ===== KPI: Average SpO2 =====
if (exists("spo2_data") && !is.null(spo2_data) && nrow(spo2_data) > 0) {
  kpi_spo2 <- round(mean(spo2_data$value, na.rm = TRUE), 1)
} else {
  kpi_spo2 <- NA
}

kpi_table <- data.frame(
  Metric = c("Average Daily Heart Rate", "Average Daily Steps", "Average Deep Sleep", "Average SpO2"),
  Value = c(
    paste(kpi_hr, "bpm"),
    paste(format(kpi_steps, big.mark = ","), "steps"),
    paste(kpi_sleep, "min"),
    paste(kpi_spo2, "%")
  )
)

kable(kpi_table)
```

### Heart Rate Over Time

Heart rate values over time shows daily patterns, resting HR trends, exercise intensity periods, and potential recovery patterns. This chart shows all days by averaged 5 minute buckets.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# For Rmd: use full dataset
# For App.R: hr_data() is already filtered by date and participant
if (exists("hr_data") && !is.null(hr_data) && nrow(hr_data) > 0) {
  chart_data <- hr_data %>%
    filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220)
  
  # Optional: Filter to specific date range if needed
  # chart_data <- chart_data %>%
  #   filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08"))
}

# ===== CHART CODE =====
# Create the ggplot object
if (exists("chart_data") && !is.null(chart_data) && nrow(chart_data) > 0) {
  hr_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = heart_rate_avg)) +
    # Raw data line - thin, semi-transparent
    geom_line(color = clr$hr, linewidth = 0.5, alpha = 0.8) +
    # Labels with clear descriptions
    labs(
      # title = "Heart Rate Over Time",
      x = NULL,
      y = "bpm"
      # To remove any label (title, x, or y), comment out or delete the line above
      # Example - to remove title only:
      # title = NULL, x = NULL, y = "bpm"
    ) +
    # Center the title
    theme(
      plot.title = element_text(hjust = 0.5)
    ) +
    dash_theme()
  
  # Convert to interactive plotly
  ggplotly(hr_timeseries_plot, tooltip = c("x", "y")) %>%
    layout(
      hoverlabel = list(bgcolor = clr$bg),
      title = list(text = "Heart Rate Over Time", x = 0.5),
      margin = list(l = 50, r = 20, t = 50, b = 40)
    )
} else {
  create_empty_plot("No heart rate data available")
}

# ===== FOR APP.R: Add to UI =====
# To use shinyfullscreen package to allow shiny app charts to full screen,
# we added library(shinyfullscreen) to app.R and we need to wrap the plotlyOutput
# in the UI section like this:
#
# shinyfullscreen::fullscreen_this(
#         plotlyOutput("plot_hr"),
#         click_to_fullscreen = TRUE
# )
#
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$plot_hr <- renderPlotly({
#   req(hr_data())
#   
#   df <- hr_data()
#   if (is.null(df) || nrow(df) == 0) {
#     return(create_empty_plot("No heart rate data available"))
#   }
#   
#   p <- ggplot(df, aes(x = datetime, y = heart_rate_avg)) +
#     geom_line(color = clr$hr, linewidth = 0.5, alpha = 0.8) +
#     labs(x = NULL, y = "bpm") +
#     # To remove title, add: title = NULL
#     # labs(title = NULL, x = NULL, y = "bpm")
#     dash_theme()
#   
#   ggplotly(p) %>% 
#     layout(hoverlabel = list(bgcolor = clr$bg),
#            margin = list(l = 50, r = 20, t = 50, b = 40))
# })
```

### Daily Steps

Daily step count with 10,000 step target line. Helps track physical activity levels and identify days meeting activity goals. This chart shows all days by summed 5 minute buckets.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# Aggregate steps by day
if (exists("steps_data") && !is.null(steps_data) && nrow(steps_data) > 0) {
  daily_steps_chart <- steps_data %>%
    mutate(date = as.Date(date)) %>%
    group_by(date) %>%
    summarise(total = sum(steps_5min, na.rm = TRUE))
  
  # Optional: Filter to specific date range if needed
  # daily_steps_chart <- daily_steps_chart %>%
  #   filter(date >= as.Date("2026-05-28"), date <= as.Date("2026-06-08"))
}

# ===== CHART CODE =====
if (exists("daily_steps_chart") && !is.null(daily_steps_chart) && nrow(daily_steps_chart) > 0) {
  steps_plot <- ggplot(daily_steps_chart, aes(x = date, y = total)) +
    geom_col(fill = clr$steps, width = 0.7, alpha = 0.9) +
    geom_hline(yintercept = 10000, linetype = "dashed", 
               color = clr$target_line, linewidth = 0.5) +
    scale_y_continuous(labels = scales::comma) +
    scale_x_date(date_labels = "%b %d") +
    labs(x = NULL, y = "steps") +
    theme(plot.title = element_text(hjust = 0.5))+
    dash_theme()
  
  # Convert to interactive plotly
  ggplotly(steps_plot, tooltip = c("x", "y")) %>%
    layout(
      hoverlabel = list(bgcolor = clr$bg),
      title = list(text = "Daily Steps Over Time", x = 0.5),
      margin = list(l = 50, r = 20, t = 50, b = 40)
    )
} else {
  create_empty_plot("No steps data available")
}

# ===== FOR APP.R: Add to UI =====
# shinyfullscreen::fullscreen_this(
#   plotlyOutput("plot_steps"),
#   click_to_fullscreen = TRUE
# )
#
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$plot_steps <- renderPlotly({
#   req(steps_data())
#   
#   df <- steps_data()
#   if (is.null(df) || nrow(df) == 0) {
#     return(create_empty_plot("No steps data available"))
#   }
#   
#   daily_steps <- df %>%
#     mutate(date = as.Date(date)) %>%
#     group_by(date) %>%
#     summarise(total = sum(steps_5min, na.rm = TRUE))
#   
#   if (nrow(daily_steps) == 0) {
#     return(create_empty_plot("No steps data for selected date range"))
#   }
#   
#   p <- ggplot(daily_steps, aes(x = date, y = total)) +
#     geom_col(fill = clr$steps, width = 0.7, alpha = 0.9) +
#     geom_hline(yintercept = 10000, linetype = "dashed", 
#                color = "#9CA3AF", linewidth = 0.5) +
#     scale_y_continuous(labels = scales::comma) +
#     scale_x_date(date_labels = "%b %d") +
#     labs(x = NULL, y = "steps") +
#     theme(plot.title = element_text(hjust = 0.5)) +
#     dash_theme()
#   
#   ggplotly(p) %>% 
#     layout(hoverlabel = list(bgcolor = clr$bg),
#            margin = list(l = 50, r = 20, t = 50, b = 40))
# })
```

### Sleep Stage Breakdown

Daily breakdown of sleep stages (Deep, REM, Light) in total minutes. Shows sleep quality patterns and helps identify factors affecting sleep architecture.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# Aggregate sleep stages per night
if (exists("sleep_data") && !is.null(sleep_data) && nrow(sleep_data) > 0) {
  sleep_summary <- sleep_data %>%
    group_by(dateOfSleep, sleep_stage) %>%
    summarise(minutes = n(), .groups = "drop") %>%
    filter(sleep_stage %in% c("deep", "rem", "light")) %>%
    mutate(
      sleep_stage = recode(sleep_stage,
                          deep = "Deep",
                          rem = "REM",
                          light = "Light"),
      dateOfSleep = as.Date(dateOfSleep)
    )
  
  # Optional: Filter to specific date range if needed
  # sleep_summary <- sleep_summary %>%
  #   filter(dateOfSleep >= as.Date("2026-05-28"), dateOfSleep <= as.Date("2026-06-08"))
}

# ===== CHART CODE =====
if (exists("sleep_summary") && !is.null(sleep_summary) && nrow(sleep_summary) > 0) {
  sleep_plot <- ggplot(sleep_summary, aes(x = dateOfSleep, y = minutes, fill = sleep_stage)) +
    geom_col(width = 0.7, alpha = 0.9) +
    scale_fill_manual(values = c(Deep = clr$deep, REM = clr$rem, Light = clr$light)) +
    scale_x_date(date_labels = "%b %d") +
    labs(x = NULL, y = "minutes") +
    # Remove title from ggplot since we'll set it in Plotly
    # labs(title = NULL, x = NULL, y = "minutes") +
    dash_theme()
  
  # Convert to interactive plotly
  ggplotly(sleep_plot, tooltip = c("x", "y", "fill")) %>%
    layout(
      hoverlabel = list(bgcolor = clr$bg),  # Remove quotes!
      title = list(text = "Daily Sleep States", x = 0.5),
      margin = list(l = 50, r = 20, t = 50, b = 40),
      legend = list(
        orientation = "h",           # Horizontal legend
        yanchor = "bottom",          # Anchor at bottom
        y = -0.15,                   # Position below chart (adjust as needed)
        xanchor = "center",          # Center horizontally
        x = 0.5                     # Center position
        #bgcolor = "rgba(255,255,255,0.8)"  # Semi-transparent background
      )
    ) %>%
    # ADD THIS: Explicitly set colors in Plotly
    style(
      marker = list(
        color = ~ifelse(sleep_stage == "Deep", clr$deep,
                 ifelse(sleep_stage == "REM", clr$rem,
                 clr$light))
      )
    )
} else {
  create_empty_plot("No sleep data available")
}

# ===== FOR APP.R: Add to UI =====
# shinyfullscreen::fullscreen_this(
#   plotlyOutput("plot_sleep"),
#   click_to_fullscreen = TRUE
# )
#
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$plot_sleep <- renderPlotly({
#   req(sleep_data())
#   
#   df <- sleep_data()
#   if (is.null(df) || nrow(df) == 0) {
#     return(create_empty_plot("No sleep data available"))
#   }
#   
#   # Aggregate sleep stages per night
#   sleep_summary <- df %>%
#     group_by(dateOfSleep, sleep_stage) %>%
#     summarise(minutes = n(), .groups = "drop") %>%
#     filter(sleep_stage %in% c("deep", "rem", "light")) %>%
#     mutate(sleep_stage = recode(sleep_stage,
#                                 deep = "Deep",
#                                 rem = "REM",
#                                 light = "Light"))
#   
#   if (nrow(sleep_summary) == 0) {
#     return(create_empty_plot("No sleep stage data available"))
#   }
#   
#   p <- ggplot(sleep_summary, aes(x = as.Date(dateOfSleep), y = minutes, fill = sleep_stage)) +
#     geom_col(width = 0.7, alpha = 0.9) +
#     scale_fill_manual(values = c(Deep = clr$deep, REM = clr$rem, Light = clr$light)) +
#     scale_x_date(date_labels = "%b %d") +
#     labs(x = NULL, y = "minutes") +
#     dash_theme()
#   
#   ggplotly(p) %>% 
#     layout(
#       hoverlabel = list(bgcolor = clr$bg),
#       title = list(text = "Daily Sleep States", x = 0.5),
#       margin = list(l = 50, r = 20, t = 50, b = 40),
#       legend = list(
#         orientation = "h",
#         yanchor = "bottom",
#         y = -0.15,
#         xanchor = "center",
#         x = 0.5,
#         bgcolor = "rgba(255,255,255,0.8)"
#       )
#     ) %>%
#     # ADD THIS: Explicitly set colors in Plotly
#     style(
#       marker = list(
#         color = ~ifelse(sleep_stage == "Deep", clr$deep,
#                  ifelse(sleep_stage == "REM", clr$rem,
#                  clr$light))
#       )
#     )
# })
```


## Heart Rate Tab

### HR Time Series with Smooth Overlay

Raw heart rate values (thin line) with a LOESS smooth trend (thick line) to reveal daily patterns and overall trend. Helps identify resting HR trends, exercise intensity periods, and potential recovery patterns.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# For Rmd: use full dataset
# For App.R: hr_data() is already filtered by date and participant
chart_data <- hr_data %>%
  filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08"))

# ===== CHART CODE =====
# Create the ggplot object
hr_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = heart_rate_avg)) +
  # Raw data line - thin, semi-transparent
  geom_line(color = clr$hr, linewidth = 0.3, alpha = 0.5) +
  # LOESS smooth trend - thicker, solid
  geom_smooth(method = "loess", span = 0.1, se = FALSE, 
              color = clr$hr, linewidth = .5, alpha = 0.9) +
  # Labels with clear descriptions
  labs(
    title = "Heart Rate Over Time",
    x = "Date and Time",
    y = "Heart Rate (beats per minute)"
  ) +
  # Format x-axis dates
  scale_x_datetime(
    date_labels = "%b %d, %H:%M",
    date_breaks = "12 hours"
  ) +
  # Format y-axis
  scale_y_continuous(
    limits = c(55, 150),
    breaks = seq(40, 150, by = 20),
    labels = scales::label_number(suffix = " bpm")
  ) +
  dash_theme() +
  theme(
    axis.text.x = element_text(size = 8),  # Makes X-axis tick labels smaller
    axis.text.y = element_text(size = 8),  # Makes Y-axis tick labels smaller
    axis.title.x = element_text(size = 9), # Optional: Makes X-axis title smaller
    axis.title.y = element_text(size = 9)  # Optional: Makes Y-axis title smaller
  )

# Convert to interactive plotly
ggplotly(hr_timeseries_plot, tooltip = c("x", "y")) %>%
  layout(
    xaxis = list(tickangle = -45),
    hoverlabel = list(bgcolor = "white", font = list(size = 10)),
    legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "right", x = 1)
  )

# ===== FOR APP.R: Add to UI =====
# To use shinyfullscreen package to allow shiny app charts to full screen,
# we added library(shinyfullscreen) to app.R and we need to wrap the plotlyOutput
# in the UI section like this:
#
# shinyfullscreen::fullscreen_this(
#         plotlyOutput("hr_timeseries"),
#         click_to_fullscreen = TRUE
# )
#
# We should do this for every chart :)
#
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hr_timeseries <- renderPlotly({
#   req(hr_data())
#   
#   # Filter out invalid HR values
#   chart_data <- hr_data() %>%
#     filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220)
#   
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No heart rate data available for selected filters"))
#   }
#   
#   hr_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = heart_rate_avg)) +
#     geom_line(color = clr$hr, linewidth = 0.3, alpha = 0.5) +
#     geom_smooth(method = "loess", span = 0.1, se = FALSE, 
#                 color = clr$hr, linewidth = 0.5, alpha = 0.9) +
#     labs(x = "Date and Time", y = "Heart Rate (beats per minute)") +
#     scale_x_datetime(date_labels = "%b %d, %H:%M", date_breaks = "12 hours") +
#     scale_y_continuous(limits = c(55, 150), breaks = seq(40, 150, by = 20)) +
#     dash_theme() +
#     theme(
#           axis.text.x = element_text(size = 8),  # Makes X-axis tick labels smaller
#           axis.text.y = element_text(size = 8),  # Makes Y-axis tick labels smaller
#           axis.title.x = element_text(size = 9), # Optional: Makes X-axis title smaller
#           axis.title.y = element_text(size = 9)  # Optional: Makes Y-axis title smaller
#     )
#   
#   ggplotly(hr_timeseries_plot, tooltip = c("x", "y")) %>%
#     layout(
#         xaxis = list(tickangle = -45),
#         hoverlabel = list(bgcolor = "white", font = list(size = 10)),
#         legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "right", x = 1)
# })
```

### Heart Rate by Hour of Day

Average heart rate for each hour of the day (e.g., 8 AM average, 9 AM average) across the selected date range. Reveals daily circadian patterns, typical resting HR during sleep, and peak activity hours.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# Extract hour from datetime, then calculate average HR per hour
chart_data <- hr_data %>%
  filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08")) %>%
  mutate(
    hour_of_day = hour(datetime),
    hour_label = sprintf("%02d:00", hour_of_day)
  ) %>%
  group_by(hour_of_day, hour_label) %>%
  summarise(
    avg_heart_rate = mean(heart_rate_avg, na.rm = TRUE),
    sd_heart_rate = sd(heart_rate_avg, na.rm = TRUE),
    .groups = "drop"
  )

# ===== CHART CODE =====
hr_by_hour_plot <- ggplot(chart_data, aes(x = hour_of_day, y = avg_heart_rate)) +
  # Column chart with error bars (standard deviation)
  geom_col(fill = clr$hr, width = 0.7, alpha = 0.8) +
  geom_errorbar(aes(ymin = avg_heart_rate - sd_heart_rate, 
                    ymax = avg_heart_rate + sd_heart_rate),
                width = 0.3, color = "#4B5563", linewidth = 0.4) +
  # Smooth trend line to show daily pattern
  geom_smooth(method = "loess", se = FALSE, color = "#1A1A2E", linewidth = 0.8, linetype = "dashed") +
  # Labels
  labs(
    title = "Average Heart Rate by Hour of Day",
    x = "Hour of Day",
    y = "Average Heart Rate (beats per minute)"
  ) +
  # X-axis: show every 2 hours
  scale_x_continuous(
    breaks = seq(0, 23, by = 2),
    labels = sprintf("%02d:00", seq(0, 23, by = 2))
  ) +
  scale_y_continuous(limits = c(55, 110), breaks = seq(55, 110, by = 10)) +
  dash_theme() +
  theme(panel.grid.major.x = element_blank())

# Convert to interactive plotly
ggplotly(hr_by_hour_plot, tooltip = c("x", "y", "ymin", "ymax")) %>%
  layout(
    hoverlabel = list(bgcolor = "white"),
    legend = list(orientation = "h", yanchor = "bottom", y = 1.02)
  )

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hr_by_hour <- renderPlotly({
#   req(hr_data())
#   
#   chart_data <- hr_data() %>%
#     filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220) %>%
#     mutate(
#       hour_of_day = hour(datetime),
#       hour_label = sprintf("%02d:00", hour_of_day)
#     ) %>%
#     group_by(hour_of_day, hour_label) %>%
#     summarise(
#       avg_heart_rate = mean(heart_rate_avg, na.rm = TRUE),
#       sd_heart_rate = sd(heart_rate_avg, na.rm = TRUE),
#       .groups = "drop"
#     )
#   
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No heart rate data available for selected filters"))
#   }
#   
#   hr_by_hour_plot <- ggplot(chart_data, aes(x = hour_of_day, y = avg_heart_rate)) +
#     geom_col(fill = clr$hr, width = 0.7, alpha = 0.8) +
#     geom_errorbar(aes(ymin = avg_heart_rate - sd_heart_rate, 
#                       ymax = avg_heart_rate + sd_heart_rate),
#                   width = 0.3, color = "#4B5563", linewidth = 0.4) +
#     geom_smooth(method = "loess", se = FALSE, color = "#1A1A2E", linewidth = 0.8, linetype = "dashed") +
#     labs(x = "Hour of Day", y = "Average Heart Rate (beats per minute)") +
#     scale_x_continuous(breaks = seq(0, 23, by = 2), labels = sprintf("%02d:00", seq(0, 23, by = 2))) +
#     scale_y_continuous(limits = c(55, 110), breaks = seq(55, 110, by = 10)) +
#     dash_theme() +
#     theme(panel.grid.major.x = element_blank())
#   
#   ggplotly(hr_by_hour_plot, tooltip = c("x", "y", "ymin", "ymax")) %>%
#     layout(hoverlabel = list(bgcolor = "white"))
# })
```

### Daily Min/Avg/Max Heart Rate

For each day, three lines: minimum HR, average HR, and maximum HR. Shows daily heart rate variability, identifies high-stress days, and reveals recovery patterns (lower resting HR indicates good recovery).

```{r, echo=FALSE, warning=FALSE, message=FALSE}

# ===== DATA PREPARATION =====
# Calculate daily min, mean, max HR
chart_data <- hr_data %>%
  filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08")) %>%
  mutate(date_only = as.Date(datetime)) %>%
  group_by(date_only) %>%
  summarise(
    min_hr = min(heart_rate_avg, na.rm = TRUE),
    avg_hr = mean(heart_rate_avg, na.rm = TRUE),
    max_hr = max(heart_rate_avg, na.rm = TRUE),
    .groups = "drop"
  )

# Reshape to long format for easier plotting with multiple lines
chart_data_long <- chart_data %>%
  pivot_longer(
    cols = c(min_hr, avg_hr, max_hr),
    names_to = "metric",
    values_to = "heart_rate"
  ) %>%
  mutate(
    metric_label = case_when(
      metric == "min_hr" ~ "Minimum HR",
      metric == "avg_hr" ~ "Average HR",
      metric == "max_hr" ~ "Maximum HR"
    ),
    metric_color = case_when(
      metric == "min_hr" ~ "#5DCAA5",   # Green for min
      metric == "avg_hr" ~ clr$hr,      # Red for average
      metric == "max_hr" ~ "#F0997B"    # Orange for max
    )
  )

# ===== CHART CODE =====
daily_hr_stats_plot <- ggplot(chart_data_long, aes(x = date_only, y = heart_rate, color = metric_label, group = metric_label)) +
  geom_line(linewidth = .5) +
  geom_point(size = 1.5, alpha = 0.7) +
  # Custom colors
  scale_color_manual(
    values = c("Minimum HR" = "#5DCAA5", "Average HR" = clr$hr, "Maximum HR" = "#F0997B")
  ) +
  # Labels
  labs(
    title = "Daily Heart Rate Statistics",
    x = "Date",
    y = "Heart Rate (beats per minute)",
    color = "Metric"
  ) +
  # Format x-axis dates
  scale_x_date(date_labels = "%b %d", date_breaks = "1 day") +
  scale_y_continuous(limits = c(40, 160), breaks = seq(40, 160, by = 20)) +
  dash_theme() +
  theme(legend.position = "bottom")

# Convert to interactive plotly
ggplotly(daily_hr_stats_plot, tooltip = c("x", "y", "color")) %>%
  layout(
    hoverlabel = list(bgcolor = "white"),
    legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "center", x = 0.5)
  )

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hr_daily_stats <- renderPlotly({
#   req(hr_data())
#   
#   chart_data <- hr_data() %>%
#     filter(!is.na(datetime), heart_rate_avg > 30, heart_rate_avg < 220) %>%
#     mutate(date_only = as.Date(datetime)) %>%
#     group_by(date_only) %>%
#     summarise(
#       min_hr = min(heart_rate_avg, na.rm = TRUE),
#       avg_hr = mean(heart_rate_avg, na.rm = TRUE),
#       max_hr = max(heart_rate_avg, na.rm = TRUE),
#       .groups = "drop"
#     )
#   
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No heart rate data available for selected filters"))
#   }
#   
#   chart_data_long <- chart_data %>%
#     pivot_longer(cols = c(min_hr, avg_hr, max_hr), names_to = "metric", values_to = "heart_rate") %>%
#     mutate(metric_label = case_when(
#       metric == "min_hr" ~ "Minimum HR",
#       metric == "avg_hr" ~ "Average HR", 
#       metric == "max_hr" ~ "Maximum HR"
#     ))
#   
#   daily_hr_stats_plot <- ggplot(chart_data_long, aes(x = date_only, y = heart_rate, color = metric_label, group = metric_label)) +
#     geom_line(linewidth = .5) +
#     geom_point(size = 1.5, alpha = 0.7) +
#     scale_color_manual(values = c("Minimum HR" = "#5DCAA5", "Average HR" = clr$hr, "Maximum HR" = "#F0997B")) +
#     labs(x = "Date", y = "Heart Rate (beats per minute)", color = "Metric") +
#     scale_x_date(date_labels = "%b %d", date_breaks = "1 day") +
#     scale_y_continuous(limits = c(40, 160), breaks = seq(40, 160, by = 20)) +
#     dash_theme() +
#     theme(legend.position = "bottom")
#   
#   ggplotly(daily_hr_stats_plot, tooltip = c("x", "y", "color")) %>%
#     layout(hoverlabel = list(bgcolor = "white"))
# })
```

## Activity Zone Minutes
Daily breakdown of minutes spent in Fat Burn, Cardio, and Peak heart rate zones.
Shows workout intensity distribution. Helps users understand if they're meeting weekly zone minute goals (typically 150+ minutes of moderate-to-vigorous activity).

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION ===== #
# Sum per day per zone type
chart_data <- zone_data %>% 
  filter(!is.na(datetime)) %>% 
  mutate(date_only = as.Date(datetime)) %>% 
  group_by(date_only) %>% 
  summarise(
    fat_burn = sum(fat_burn_minutes, na.rm = TRUE),
    cardio = sum(cardio_minutes, na.rm = TRUE),
    peak = sum(peak_minutes, na.rm = TRUE),
    total_active = fat_burn + cardio + peak,
    .groups = "drop"
  ) %>% 
  filter(date_only >= as.Date("2026-05-28"), date_only <= as.Date("2026-06-08"))

# Reshape to long format for stacked bar chart
chart_data_long <- chart_data %>% 
  pivot_longer(
    cols = c(fat_burn, cardio, peak), 
    names_to = "zone", 
    values_to = "minutes"
  ) %>% 
  mutate(
    zone_label = case_when(
      zone == "fat_burn" ~ "Fat Burn Zone",
      zone == "cardio" ~ "Cardio Zone",
      zone == "peak" ~ "Peak Zone"
    )
  )

# ===== CHART CODE ===== #
zone_minutes_plot <- ggplot(chart_data_long, aes(x = date_only, y = minutes, fill = zone_label)) +
  # Stacked bars
  geom_col(width = 0.7, alpha = 0.9) + 
  # Custom zone colors
  scale_fill_manual(
    values = c("Fat Burn Zone" = "#85B7EB", "Cardio Zone" = "#F0A500", "Peak Zone" = "#E24B4A")
  ) + 
  # FIX: Explicitly map x = date_only inside geom_text
  geom_text(
    aes(x = date_only, label = ifelse(total_active > 0, total_active, NA), y = total_active + 2),
    data = filter(chart_data_long, zone == "peak"), 
    inherit.aes = FALSE,
    size = 3, 
    color = "#4B5563", 
    vjust = 0
  ) + 
  labs(
    title = "Daily Active Zone Minutes", 
    x = "Date", 
    y = "Minutes", 
    fill = "Heart Rate Zone",
    caption = "Fat Burn (50-69% max HR) | Cardio (70-84% max HR) | Peak (85-100% max HR)"
  ) + 
  # Reference target line
  geom_hline(yintercept = 21, linetype = "dashed", color = "#5DCAA5", linewidth = 0.5, alpha = 0.7) + 
  annotate("text", x = min(chart_data$date_only), y = 23, label = "Daily target (150 min/week)", hjust = 0, size = 2.5, color = "#5DCAA5") + 
  scale_x_date(date_labels = "%b %d", date_breaks = "1 day") + 
  scale_y_continuous(limits = c(0, max(chart_data$total_active, na.rm = TRUE) + 15), breaks = seq(0, 100, by = 20)) + 
  dash_theme()

# Convert to interactive plotly
ggplotly(zone_minutes_plot, tooltip = c("x", "y", "fill")) %>% 
  layout(
    autosize = TRUE,
    hoverlabel = list(bgcolor = "white"),
    legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "center", x = 0.5)
  )

# ===== FOR APP.R: Add to UI ===== #
# shinyfullscreen::fullscreen_this(
#   plotlyOutput("zone_minutes_chart"),
#   click_to_fullscreen = TRUE
# )

# ===== FOR APP.R: Wrap in renderPlotly ===== #
# output$zone_minutes_chart <- renderPlotly({
#   req(zone_minutes_data())
#   
#   chart_data_shiny <- zone_minutes_data() %>%
#     filter(!is.na(datetime)) %>%
#     mutate(date_only = as.Date(datetime)) %>%
#     group_by(date_only) %>%
#     summarise(
#       fat_burn = sum(fat_burn_minutes, na.rm = TRUE),
#       cardio = sum(cardio_minutes, na.rm = TRUE),
#       peak = sum(peak_minutes, na.rm = TRUE),
#       total_active = fat_burn + cardio + peak,
#       .groups = "drop"
#     )
#   
#   if (nrow(chart_data_shiny) == 0) {
#     return(create_empty_plot("No zone minutes data available for selected filters"))
#   }
#   
#   chart_data_long_shiny <- chart_data_shiny %>%
#     pivot_longer(cols = c(fat_burn, cardio, peak), names_to = "zone", values_to = "minutes") %>%
#     mutate(zone_label = case_when(
#       zone == "fat_burn" ~ "Fat Burn Zone",
#       zone == "cardio" ~ "Cardio Zone",
#       zone == "peak" ~ "Peak Zone"
#     ))
#   
#   zone_minutes_plot_shiny <- ggplot(chart_data_long_shiny, aes(x = date_only, y = minutes, fill = zone_label)) +
#     geom_col(width = 0.7, alpha = 0.9) +
#     scale_fill_manual(values = c("Fat Burn Zone" = "#85B7EB", "Cardio Zone" = "#F0A500", "Peak Zone" = "#E24B4A")) +
#     # FIX: Explicitly map x = date_only here too for the shiny app server block
#     geom_text(
#       aes(x = date_only, label = ifelse(total_active > 0, total_active, NA), y = total_active + 2),
#       data = filter(chart_data_long_shiny, zone == "peak"), inherit.aes = FALSE, size = 3, color = "#4B5563", vjust = 0
#     ) +
#     labs(x = "Date", y = "Minutes", fill = "Heart Rate Zone",
#          caption = "Fat Burn (50-69% max HR) | Cardio (70-84% max HR) | Peak (85-100% max HR)") +
#     geom_hline(yintercept = 21, linetype = "dashed", color = "#5DCAA5", linewidth = 0.5, alpha = 0.7) +
#     scale_x_date(date_labels = "%b %d", date_breaks = "1 day") +
#     scale_y_continuous(limits = c(0, max(chart_data_shiny$total_active, na.rm = TRUE) + 15)) +
#     dash_theme()
#   
#   ggplotly(zone_minutes_plot_shiny, tooltip = c("x", "y", "fill")) %>% 
#     layout(
#       autosize = TRUE,
#       hoverlabel = list(bgcolor = "white"),
#       legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "center", x = 0.5)
#     )
# })
```

## Admin: HRV Time Series (Heart Rate Variability)

RMSSD values over time. Higher HRV indicates better recovery and parasympathetic nervous system activation. Tracks recovery status. Low HRV may indicate stress, fatigue, or over-training. High HRV (relative to baseline) suggests good recovery.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION =====
# HRV data is less frequent (typically every 5 minutes during sleep)
chart_data <- hrv_data %>%
  filter(datetime >= as.POSIXct("2026-05-28"), datetime <= as.POSIXct("2026-06-08"))

# Calculate baseline (rolling average) for comparison
chart_data <- chart_data %>%
  arrange(datetime) %>%
  mutate(
    rolling_avg = zoo::rollapply(rmssd_ms, width = 10, FUN = mean, fill = NA, align = "center")
  )

# ===== CHART CODE =====
hrv_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = rmssd_ms)) +
  # Raw HRV points
  geom_point(color = clr$hr, alpha = 0.4, size = 1) +
  # LOESS smooth trend
  geom_smooth(method = "loess", se = TRUE, fill = "#E24B4A20", 
              color = clr$hr, linewidth = 1) +
  # Rolling average line (optional overlay)
  geom_line(aes(y = rolling_avg), color = "#1A1A2E", linewidth = 0.5, alpha = 0.6, na.rm = TRUE) +
  # Reference line for typical HRV baseline (adjust based on participant)
  geom_hline(yintercept = 20, linetype = "dashed", color = "#9CA3AF", linewidth = 0.4, alpha = 0.7) +
  # Annotations
  annotate("text", x = min(chart_data$datetime), y = 22, 
           label = "Typical baseline", hjust = 0, size = 3, color = "#6B7280") +
  # Labels
  labs(
    title = "Heart Rate Variability (HRV) Over Time",
    x = "Date and Time",
    y = "RMSSD (milliseconds)",
    caption = "Higher HRV indicates better recovery | Lower HRV may indicate stress or fatigue"
  ) +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "1 day") +
  scale_y_continuous(limits = c(0, 60), breaks = seq(0, 60, by = 10)) +
  dash_theme()

# Convert to interactive plotly
ggplotly(hrv_timeseries_plot, tooltip = c("x", "y")) %>%
  layout(
    hoverlabel = list(bgcolor = "white"),
    annotations = list(
      x = 0, y = -0.15, xref = "paper", yref = "paper",
      text = "Higher HRV = better recovery",
      showarrow = FALSE,
      font = list(size = 10, color = "#6B7280")
    )
  )

# ===== FOR APP.R: Add to UI =====
# Check previous chart ^ for fullscreen code
# ===== FOR APP.R: Wrap in renderPlotly =====
# output$hrv_chart <- renderPlotly({
#   req(hrv_data())
#   
#   chart_data <- hrv_data() %>%
#     filter(!is.na(datetime), rmssd_ms > 0, rmssd_ms < 200)
#   
#   if (nrow(chart_data) == 0) {
#     return(create_empty_plot("No HRV data available for selected filters"))
#   }
#   
#   # Calculate rolling average (need zoo package)
#   # library(zoo) - add to app.R
#   chart_data <- chart_data %>%
#     arrange(datetime) %>%
#     mutate(rolling_avg = zoo::rollapply(rmssd_ms, width = min(10, n()), FUN = mean, fill = NA, align = "center"))
#   
#   hrv_timeseries_plot <- ggplot(chart_data, aes(x = datetime, y = rmssd_ms)) +
#     geom_point(color = clr$hr, alpha = 0.4, size = 1) +
#     geom_smooth(method = "loess", se = TRUE, fill = "#E24B4A20", color = clr$hr, linewidth = 1) +
#     geom_line(aes(y = rolling_avg), color = "#1A1A2E", linewidth = 0.5, alpha = 0.6, na.rm = TRUE) +
#     geom_hline(yintercept = 20, linetype = "dashed", color = "#9CA3AF", linewidth = 0.4) +
#     labs(x = "Date and Time", y = "RMSSD (milliseconds)", 
#          caption = "Higher HRV indicates better recovery | Lower HRV may indicate stress or fatigue") +
#     scale_x_datetime(date_labels = "%b %d", date_breaks = "1 day") +
#     scale_y_continuous(limits = c(0, 60), breaks = seq(0, 60, by = 10)) +
#     dash_theme()
#   
#   ggplotly(hrv_timeseries_plot, tooltip = c("x", "y")) %>%
#     layout(hoverlabel = list(bgcolor = "white"))
# })
```

## Sleep Tab

### Hypnogram
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# ===== DATA PREPARATION ===== #
target_date <- as.Date("2026-05-31")

# Identify all sleep sessions and find the primary (longest) one
sleep_sessions <- sleep_minute %>%
  filter(dateOfSleep == target_date) %>%
  group_by(logId) %>%
  summarise(
    session_start = min(as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")),
    session_end = max(as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")),
    duration_minutes = n(),
    .groups = "drop"
  ) %>%
  mutate(
    session_label = paste(format(session_start, "%H:%M"), "-", format(session_end, "%H:%M")),
    session_choice = paste(session_label, "(", duration_minutes, "min)")
  )

# For markdown, use the primary session (longest)
primary_session_id <- sleep_sessions$logId[which.max(sleep_sessions$duration_minutes)]

# Prepare hypnogram data for primary session
hypnogram_data <- sleep_minute %>%
  filter(dateOfSleep == target_date) %>%
  filter(logId == primary_session_id) %>%
  filter(sleep_stage %in% c("wake", "light", "deep", "rem", "asleep")) %>%
  mutate(
    datetime_utc = as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC"),
    time_num = hour(datetime_utc) + minute(datetime_utc) / 60,
    stage_numeric = case_when(
      sleep_stage == "wake" ~ 4,
      sleep_stage == "rem" ~ 3,
      sleep_stage == "light" ~ 2,
      sleep_stage == "deep" ~ 1,
      sleep_stage == "asleep" ~ 2
    ),
    stage_label = case_when(
      sleep_stage == "wake" ~ "Wake",
      sleep_stage == "rem" ~ "REM",
      sleep_stage == "light" ~ "Light",
      sleep_stage == "deep" ~ "Deep",
      sleep_stage == "asleep" ~ "Asleep"
    )
  )

# ===== CHART CODE ===== #
hypnogram_plot <- ggplot(hypnogram_data, aes(x = time_num, y = stage_numeric)) +
  geom_line(color = "#2C3E50", linewidth = .5) +
  geom_point(aes(color = stage_label), size = 2, alpha = 0.7) +
  scale_color_manual(
    values = c(
      "Wake" = "#E74C3C",
      "REM" = "#3498DB",
      "Light" = "#F39C12",
      "Deep" = "#2ECC71",
      "Asleep" = "#95A5A6"
    )
  ) +
  scale_y_continuous(
    breaks = 4:1,
    labels = c("Wake", "REM", "Light", "Deep"),
    limits = c(0.5, 4.5)
  ) +
  scale_x_continuous(
    breaks = seq(0, 24, 2),
    limits = c(0, 24),
    labels = c("12 AM", "2 AM", "4 AM", "6 AM", "8 AM", "10 AM", 
               "12 PM", "2 PM", "4 PM", "6 PM", "8 PM", "10 PM", "12 AM")
  ) +
  labs(
    title = paste("Sleep Hypnogram -", format(target_date, "%B %d, %Y")),
    subtitle = ifelse(nrow(sleep_sessions) > 1, 
                      paste(nrow(sleep_sessions), "sleep sessions detected. Showing primary session."),
                      ""),
    x = "Time",
    y = "Sleep Stage",
    color = "Stage"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "gray90", linetype = "dotted"),
    plot.title = element_text(face = "bold", size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

ggplotly(hypnogram_plot, tooltip = c("x", "y", "colour")) %>%
  layout(
      autosize = TRUE,
    hoverlabel = list(bgcolor = "white"),
    legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "center", x = 0.5)
  )

# ===== FOR APP.R: Add to UI ===== #
# In UI, add:
# selectInput("sleep_session", "Select Sleep Session", choices = NULL)
#
# shinyfullscreen::fullscreen_this(
#   plotlyOutput("hypnogram_chart"),
#   click_to_fullscreen = TRUE
# )

# ===== FOR APP.R: Wrap in renderPlotly ===== #
# output$hypnogram_chart <- renderPlotly({
#   req(sleep_data(), input$hypnogram_date)
#   
#   target_date_shiny <- as.Date(input$hypnogram_date)
#   
#   # Identify all sleep sessions and create dropdown choices
#   sleep_sessions_shiny <- sleep_data() %>%
#     filter(dateOfSleep == target_date_shiny) %>%
#     group_by(logId) %>%
#     summarise(
#       session_start = min(as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")),
#       session_end = max(as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")),
#       duration_minutes = n(),
#       .groups = "drop"
#     ) %>%
#     mutate(
#       session_label = paste(format(session_start, "%H:%M"), "-", format(session_end, "%H:%M")),
#       session_choice = paste(session_label, "(", duration_minutes, "min)")
#     )
#   
#   # Update dropdown choices
#   updateSelectInput(session, "sleep_session", 
#                     choices = setNames(sleep_sessions_shiny$logId, sleep_sessions_shiny$session_choice),
#                     selected = sleep_sessions_shiny$logId[1])
#   
#   # Get selected session
#   selected_session <- input$sleep_session
#   
#   # If nothing selected yet, use first session
#   if(is.null(selected_session)) {
#     selected_session <- sleep_sessions_shiny$logId[1]
#   }
#   
#   # Prepare hypnogram data for selected session
#   hypnogram_data_shiny <- sleep_data() %>%
#     filter(dateOfSleep == target_date_shiny) %>%
#     filter(logId == selected_session) %>%
#     filter(sleep_stage %in% c("wake", "light", "deep", "rem", "asleep")) %>%
#     mutate(
#       datetime_utc = as.POSIXct(datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC"),
#       time_num = hour(datetime_utc) + minute(datetime_utc) / 60,
#       stage_numeric = case_when(
#         sleep_stage == "wake" ~ 4,
#         sleep_stage == "rem" ~ 3,
#         sleep_stage == "light" ~ 2,
#         sleep_stage == "deep" ~ 1,
#         sleep_stage == "asleep" ~ 2
#       ),
#       stage_label = case_when(
#         sleep_stage == "wake" ~ "Wake",
#         sleep_stage == "rem" ~ "REM",
#         sleep_stage == "light" ~ "Light",
#         sleep_stage == "deep" ~ "Deep",
#         sleep_stage == "asleep" ~ "Asleep"
#       )
#     )
#   
#   if (nrow(hypnogram_data_shiny) == 0) {
#     return(create_empty_plot(paste("No sleep stage data for", target_date_shiny)))
#   }
#   
#   # Get selected session label for subtitle
#   selected_label <- sleep_sessions_shiny %>%
#     filter(logId == selected_session) %>%
#     pull(session_label)
#   
#   hypnogram_plot_shiny <- ggplot(hypnogram_data_shiny, aes(x = time_num, y = stage_numeric)) +
#     geom_line(color = "#2C3E50", linewidth = 1.2) +
#     geom_point(aes(color = stage_label), size = 2, alpha = 0.7) +
#     scale_color_manual(values = c("Wake" = "#E74C3C", "REM" = "#3498DB", 
#                                   "Light" = "#F39C12", "Deep" = "#2ECC71", "Asleep" = "#95A5A6")) +
#     scale_y_continuous(breaks = 4:1, labels = c("Wake", "REM", "Light", "Deep"), limits = c(0.5, 4.5)) +
#     scale_x_continuous(breaks = seq(0, 24, 2), limits = c(0, 24),
#                        labels = c("12 AM", "2 AM", "4 AM", "6 AM", "8 AM", "10 AM", 
#                                   "12 PM", "2 PM", "4 PM", "6 PM", "8 PM", "10 PM", "12 AM")) +
#     labs(title = paste("Sleep Hypnogram -", format(target_date_shiny, "%B %d, %Y")),
#          subtitle = paste("Session:", selected_label),
#          x = "Time", y = "Sleep Stage", color = "Stage") +
#     theme_minimal(base_size = 12) +
#     theme(legend.position = "bottom", panel.grid.minor = element_blank(),
#           panel.grid.major.x = element_line(color = "gray90", linetype = "dotted"),
#           plot.title = element_text(face = "bold", size = 14),
#           axis.text.x = element_text(angle = 45, hjust = 1))
#   
#   ggplotly(hypnogram_plot_shiny, tooltip = c("x", "y", "colour")) %>%
#     layout(hoverlabel = list(bgcolor = "white"),
#            legend = list(orientation = "h", yanchor = "bottom", y = 1.02, xanchor = "center", x = 0.5))
# })
```